---
title: "Kerala Analysis - 1"
author: "Najah"
date: "12/03/2021"
params:
  orig_date: 'Original Publish Date: 12 March, 2020'
  update_date: !r paste("Updated on:", format(Sys.time(), '%d %B, %Y'))
output:
  html_document:
    theme: flatly
    toc: TRUE
    toc_float: TRUE
    toc_depth: 4
    number_sections: false
    fig_width: 6            
editor_options: 
  chunk_output_type: inline
---

<style>
    body .main-container {
        max-width: 1000px;
    }
</style>

------------------------------------------------------------------------

### Document History

`r params$orig_date`

`r params$update_date`

------------------------------------------------------------------------


```{r set up, warning=FALSE, include=FALSE, message= FALSE }

knitr::opts_chunk$set(cache = TRUE,echo = FALSE, message=FALSE, warning = FALSE,fig.width = 16/2, fig.height = 9/2)

library(data.table)
library(tidyverse)
library(kableExtra)
library(cowplot)

`%!in%` = Negate(`%in%`)

select <- dplyr::select
```


The state has 140 Assembly seats and 20 Loksabha seats. Since 1980, elections are fought between two major electoral alliances - UDF and LDF. These two alliances have been dominating the electoral space leading to a bi-polar political contests in both AE & GE. I've listed the major allies of these two coalition below:

- LDF
  - CPI
  - CPM
- UDF
  - IUML
  - KEC(M)
  - RSP

There is only 11 reserved seats in the state.


----




```{r reading files}

ge <- fread("D:/cpr/data/tcpd/TCPD_GE_all.csv")


ge_kl <- ge %>% filter (State_Name == "Kerala")


ae_kl <- fread("D:/cpr/data/tcpd/states/Kerala_2020.csv")

ae_ge_kl <- rbind(ge_kl, ae_kl)


names(ae_ge_kl) <- tolower(names(ae_ge_kl) )

ae_ge_kl <-  ae_ge_kl %>% filter(poll_no ==0 & party != "NOTA")

```



##  Turnout



```{r}

ae_ge_kl %>% filter(position==1) %>% group_by(election_type, year) %>% summarise(turnout = mean(turnout_percentage, na.rm=TRUE)) %>% 
  ggplot(aes(year, turnout, color = election_type))+
  geom_point()+
  geom_line(size = 1)+
  ylim(50,90)+
  colorspace::scale_colour_discrete_qualitative(palette = "Dark 2")+

  labs(title = "Turnout Percentage",subtitle = "AE & GE",  x = "Years", y = "Average Turnout (%)", fill = "Election Type" )+

  theme_minimal()+
  theme(plot.margin = unit(c(.5,.5,.5,.5), "cm"),
        legend.position = "bottom",
        plot.background = element_blank(),
        plot.title = element_text( size = 18, family = "serif"),
        plot.subtitle = element_text( size = 15,color = "grey50",
                                     margin = margin(t = 0, r = 0, b = 20, l = 0)),
        text = element_text(color = "gray20",family = "serif"),
        axis.text.x = element_text( 
                                   hjust = .5, vjust = 0),
        legend.title = element_blank(),
        legend.text = element_text(size = 12),
        axis.text = element_text(face = "italic", size = 10),
        axis.title = element_text(vjust = -1, size = 15),        
        axis.ticks = element_blank(),
        panel.grid.major = element_line(color = "gray50", size = .5),
        panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
         axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
        #axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        axis.line.x = element_line(),
        axis.title.x = element_blank()
  ) 

  
 # colorspace::hcl_palettes(plot = TRUE)

```


## Vicotry margin


```{r}

ae_ge_kl %>% filter(position ==1) %>% group_by(election_type, year) %>% summarise(mv = mean(margin_percentage, na.rm  =TRUE)) %>% 
  ggplot(aes(year,mv, color = election_type,group = election_type))+
  geom_line(size =1)+
    labs(title = "Average victory margin",subtitle = "AE GE",  x = "Years", y = "Margin (%)", fill = "Election Type")+
colorspace::scale_colour_discrete_qualitative(palette = "Dark 2")+
  theme_minimal()+
  
  theme(plot.margin = unit(c(.5,.5,.5,.5), "cm"),
        legend.position = "bottom",
        plot.background = element_blank(),
        plot.title = element_text( size = 18, family = "serif"),
        plot.subtitle = element_text( size = 15,color = "grey50",
                                     margin = margin(t = 0, r = 0, b = 20, l = 0)),
        text = element_text(color = "gray20",family = "serif"),
        axis.text.x = element_text( 
                                   hjust = .5, vjust = 0),
        legend.title = element_blank(),
        legend.text = element_text(size = 12),
        axis.text = element_text(face = "italic", size = 10),
        axis.title = element_text(vjust = -1, size = 15),        
        axis.ticks = element_blank(),
        panel.grid.major = element_line(color = "gray50", size = .5),
        panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
         axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
       # axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        axis.line.x = element_line(),
        axis.title.x = element_blank()
  )+
  ylim(0,20)




```

# Party Performance


## Party vote share


### GE



```{r alliance}
#unique( ae_ge_kl$party[ae_ge_kl$position%in% c(1) &ae_ge_kl$year >1980])


ae_ge_kl <- ae_ge_kl %>% mutate(party_1= case_when (party %in% c("MUL", "INL", "IUML") ~"IUML",
                                                    TRUE ~party))


ae_ge_kl  <- ae_ge_kl %>% mutate(front= case_when (party %in% c("KEC(M)","KEC(J)",  "INC", "IUML", "MUL","KCM", "RSP","RSPK(B)","KCS","MPKSC", "IML","NDP")  ~"UDF",
                    party %in% c("CPI", "CPM", "JD(S)", "JD","NCP","C(S)","NSC", "CMPKSC","KEC(B)","CPIM","INL","KCST", "LJD","JPSS","DIC","NSC")  ~"LDF",
                    party %in% c("BJP","JD(U)","IFDP") & year == 2016 ~"NDA",
                    TRUE ~party
                    ))
```



```{r}
ae_ge_kl <- ae_ge_kl %>% group_by(election_type,year)%>% mutate(tot_votes_yr = sum(votes))

ae_ge_kl %>% ungroup() %>% filter(election_type == "GE" &year >1980 & party_1 %in% c("INC", "CPI", "CPM", "IUML","KEC(M)", "BJP")) %>% group_by(election_type,year,party_1) %>% summarise(vs = sum(votes)/tot_votes_yr*100) %>% distinct(election_type, year, party_1, .keep_all = TRUE) %>% 
  ggplot(aes(factor(year), vs, color = party_1, group= party_1))+
  
  geom_line(size =1)+
  geom_point(color = "black")+
  ylim(0,50)+
  #facet_wrap(~election_type, ncol =1)+
  colorspace::scale_colour_discrete_qualitative(palette = "Dark 2")+

  labs(title = "Vote share  of major parties",subtitle = "GE 1980:2019",  x = "Years", y = "Vote share (%)", fill = "Election Type" )+
  scale_color_manual(values = c(
                                "INC" = "steelblue",
                                "CPM" = "red",
                                "IUML" = "chartreuse4",
                                 "CPI" = "brown",
                                "KEC(M)" = "cyan2",
                                "BJP" = "darkorange1"))+

  theme_minimal()+
  theme(plot.margin = unit(c(.5,.5,.5,.5), "cm"),
        legend.position = "bottom",
        plot.background = element_blank(),
        plot.title = element_text( size = 18, family = "serif"),
        plot.subtitle = element_text( size = 15,color = "grey50",
                                     margin = margin(t = 0, r = 0, b = 20, l = 0)),
        text = element_text(color = "gray20",family = "serif"),
        axis.text.x = element_text( 
                                   hjust = .5, vjust = 0),
        legend.title = element_blank(),
        legend.text = element_text(size = 12),
        axis.text = element_text(face = "italic", size = 10),
        axis.title = element_text(vjust = -1, size = 15),        
        axis.ticks = element_blank(),
        panel.grid.major = element_line(color = "gray", size = .5),
        panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
         axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
       # axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        axis.line.x = element_line(),
        axis.title.x = element_blank()
  ) 


```

---

### AE

```{r}
ae_ge_kl %>% ungroup() %>% filter(election_type == "AE" &year >1980 & party_1 %in% c("INC", "CPI", "CPM", "IUML","KEC(M)", "BJP")) %>% group_by(election_type,year,party_1) %>% summarise(vs = sum(votes)/tot_votes_yr*100) %>% distinct(election_type, year, party_1, .keep_all = TRUE) %>% 
  ggplot(aes(factor(year), vs, color = party_1, group= party_1))+
  
  geom_line(size =1)+
  geom_point(color = "grey50")+
  ylim(0,40)+
  #facet_wrap(~election_type, ncol =1)+
  #colorspace::scale_colour_discrete_qualitative(palette = "Dark 2")+

  labs(title = "Vote share  of major parties",subtitle = "AE 1980:2016",  x = "Years", y = "Vote share (%)", fill = "Election Type" )+
  scale_color_manual(values = c(
                                "INC" = "steelblue",
                                "CPM" = "red",
                                "IUML" = "chartreuse4",
                                 "CPI" = "brown",
                                "KEC(M)" = "cyan2",
                                "BJP" = "darkorange1"))+

  theme_minimal()+
  theme(plot.margin = unit(c(.5,.5,.5,.5), "cm"),
        legend.position = "bottom",
        plot.background = element_blank(),
        plot.title = element_text( size = 18, family = "serif"),
        plot.subtitle = element_text( size = 15,color = "grey50",
                                     margin = margin(t = 0, r = 0, b = 20, l = 0)),
        text = element_text(color = "gray20",family = "serif"),
        axis.text.x = element_text( 
                                   hjust = .5, vjust = 0),
        legend.title = element_blank(),
        legend.text = element_text(size = 12),
        axis.text = element_text(face = "italic", size = 10),
        axis.title = element_text(vjust = -1, size = 15),        
        axis.ticks = element_blank(),
        panel.grid.major = element_line(color = "gray", size = .5),
        panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
         axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
       # axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        axis.line.x = element_line(),
        axis.title.x = element_blank()
  ) 

```

---

## seat share

### GE

```{r}
ae_ge_kl %>% ungroup() %>% filter(election_type == "GE" &year >1980 & party_1 %in% c("INC", "CPI", "CPM", "IUML","KEC(M)", "BJP")& position==1) %>% group_by(election_type,year,party_1) %>% summarise( n_seats = n(), seats_pc = (n_seats /20) *100) %>% 
  ggplot(aes(factor(year), seats_pc, color = party_1, group = party_1))+
  
  geom_line(size =1)+
  geom_point(color = "black")+
  
  #facet_wrap(~election_type, ncol =1)+
  #colorspace::scale_colour_discrete_qualitative(palette = "Dark 2")+

  labs(title = "Seat share  of major parties",subtitle = "GE 1980:2019",  x = "Years", y = "Seat share (%)", fill = "Election Type" )+
  scale_color_manual(values = c(
                                "INC" = "steelblue",
                                "CPM" = "red",
                                "IUML" = "chartreuse4",
                                 "CPI" = "brown",
                                "KEC(M)" = "cyan2",
                                "BJP" = "darkorange1"))+

  theme_minimal()+
  
  theme(plot.margin = unit(c(.5,.5,.5,.5), "cm"),
        legend.position = "bottom",
        plot.background = element_blank(),
        plot.title = element_text( size = 18, family = "serif"),
        plot.subtitle = element_text( size = 15,color = "grey50",
                                     margin = margin(t = 0, r = 0, b = 20, l = 0)),
        text = element_text(color = "gray20",family = "serif"),
        axis.text.x = element_text( 
                                   hjust = .5, vjust = 0),
        legend.title = element_blank(),
        legend.text = element_text(size = 12),
        axis.text = element_text(face = "italic", size = 10),
        axis.title = element_text(vjust = -1, size = 15),        
        axis.ticks = element_blank(),
        panel.grid.major = element_line(color = "gray50", size = .5),
        panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
         axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
       # axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        axis.line.x = element_line(),
        axis.title.x = element_blank()
  ) +
  
  ylim(0,80)

```

---

### AE

```{r}
ae_ge_kl %>% ungroup() %>% filter(election_type == "AE" &year >1980 & party_1 %in% c("INC", "CPI", "CPM", "IUML","KEC(M)", "BJP")& position==1) %>% group_by(election_type,year,party_1) %>% summarise( n_seats = n(), seats_pc = (n_seats /140) *100) %>% 
  ggplot(aes(factor(year), seats_pc, color = party_1, group = party_1))+
  
  geom_line(size =1)+
  geom_point()+
  
  #facet_wrap(~election_type, ncol =1)+
  #colorspace::scale_colour_discrete_qualitative(palette = "Dark 2")+

  labs(title = "Seat share  of major parties",subtitle = "AE 1980:2016",  x = "Years", y = "Seat share (%)", fill = "Election Type" )+
  scale_color_manual(values = c(
                                "INC" = "steelblue",
                                "CPM" = "red",
                                "IUML" = "chartreuse4",
                                 "CPI" = "brown",
                                "KEC(M)" = "cyan2",
                                "BJP" = "darkorange1"))+

  theme_minimal()+
  
  theme(plot.margin = unit(c(.5,.5,.5,.5), "cm"),
        legend.position = "bottom",
        plot.background = element_blank(),
        plot.title = element_text( size = 18, family = "serif"),
        plot.subtitle = element_text( size = 15,color = "grey50",
                                     margin = margin(t = 0, r = 0, b = 20, l = 0)),
        text = element_text(color = "gray20",family = "serif"),
        axis.text.x = element_text( 
                                   hjust = .5, vjust = 0),
        legend.title = element_blank(),
        legend.text = element_text(size = 12),
        axis.text = element_text(face = "italic", size = 10),
        axis.title = element_text(vjust = -1, size = 15),        
        axis.ticks = element_blank(),
        panel.grid.major = element_line(color = "gray50", size = .5),
        panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
         axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
       # axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        axis.line.x = element_line(),
        axis.title.x = element_blank()
  ) +
  
  ylim(0,50)
```



```{r}
## reading pc files

ac_19 <- readxl::read_xls("D:/cpr/data/GE_PC_AC-main/2019_AC_PC.xls")

ac_14 <-  readxl::read_xlsx("D:/cpr/data/GE_PC_AC-main/2014_AC_PC.xlsx")

#ac_19 <- ac_19 %>% group_by(`State-UT Code & Name`, `AC NO`) %>% mutate(ac_votes=(sum(`VOTES SECURED EVM`, na.rm = TRUE)))

## not filtering nota and ind now since that is needed to calculate votes

kl_19 <- ac_19 %>% filter(`State-UT Code & Name` == "Kerala" ) %>% ungroup()

names(kl_19) <- tolower(names(kl_19))


kl_19 <- kl_19 %>% rename(state_name = `state-ut code & name`, pc_no = `pc no` , pc_name = `pc name`, constituency_no = `ac no`, constituency_name = `ac name`, electors = `total electors`, candidate = `candidate name`,votes = `votes secured evm`)

kl_19<- kl_19 %>% group_by(year, constituency_no) %>% mutate(election_type = "GE",valid_votes=sum(votes, na.rm = TRUE), vote_share_percentage =( votes/valid_votes)*100,
                                                                   turnout_percentage = (valid_votes/electors)*100) %>% ungroup()

 kl_19  <- kl_19  %>% group_by(year, constituency_no) %>%  mutate(position = order(order(vote_share_percentage, decreasing=TRUE))) %>% ungroup()
 
 
#unique (kl_19$party[kl_19$position==1])

kl_19 <- kl_19 %>% mutate(front = case_when(party %in% c("INC","RSP", "KEC(M)","IMUL","CMPKSC") ~"UDF",
                                   party %in% c("CPI","CPIM") ~"LDF",
                                   candidate %in% c("P.V. Anvar Puthan Veetil","Adv, JOICE GEORGE" )~"LDF",
                                   party %in% c("BJP", "BDJS","KEC" ) ~"NDA",
                 TRUE ~ "OTHERS"))

# 
# kl_19$party 
# 
# #kl_19 %>% filter( str_detect(candidate, "george",regex(ignore_case = TRUE) )
# 
# 
# kl_19 %>% filter(pc_name == "Idukki")

```


```{r}
kl_14 <- ac_14 %>% filter(`State-UT Code & Name` == "Kerala" )

names(kl_14) <- tolower(names(kl_14))



kl_14 <- kl_14 %>% rename(state_name = `state-ut code & name`, pc_no = pcno, pc_name = `pc name`, constituency_no = `ac no`, constituency_name = `ac name`, electors = `total electors in ac`, candidate = `candidate name`,votes = `votessecured evm`)


kl_14<- kl_14 %>% group_by(year, constituency_no) %>% mutate(election_type = "GE",valid_votes=sum(votes, na.rm = TRUE), vote_share_percentage =( votes/valid_votes)*100,
                                                                   turnout_percentage = (valid_votes/electors)*100) %>% ungroup()

 kl_14  <- kl_14  %>% group_by(year, constituency_no) %>%  mutate(position = order(order(vote_share_percentage, decreasing=TRUE))) %>% ungroup()
 
 
unique (kl_14$party[kl_14$position==1])

kl_14 <- kl_14 %>% mutate(front = case_when(party %in% c("INC","RSP", "KEC(M)","SJD", "IUML","CMPKSC") ~"UDF",
                                   party %in% c("CPI","CPM","JD(S)") ~"LDF",
                                   candidate %in% c("V.ABDURAHMAN","Adv, JOICE GEORGE", "INNOCENT","DR. CHRISTY FERNANDEZ",  "ADV. PEELIPOSE THOMAS")~"LDF",
                                   party %in% c("BJP","RSPK(B)" ) ~"NDA",
                 TRUE ~ "OTHERS"))

#kl_14 %>% filter(grepl("peelipose", candidate, ignore.case = TRUE))

```


```{r}
kl_14_19 <- rbindlist(list(kl_14,kl_19), use.names = FALSE)
```




```{r}




names(ae_kl) <- tolower(names(ae_kl))

kl_11<- ae_kl %>% filter(year %in% c(2011) & poll_no ==0 & party != "NOTA")

#unique(kl_11$party)

kl_11 <- kl_11 %>% mutate(front = case_when(party %in% c("INC", "KEC(M)","SJD", "MUL" , "KEC(J)","JD(U)","CMPKSC") ~"UDF",
                                   party %in% c("CPI","CPM","JD(S)","NCP", "INL","C(S)") ~"LDF",
                                   candidate %in% c("A.A. AZEEZ","SHIBU BABY JOHN")~"UDF",
                                   candidate %in% c("KOVOOR KUNJUMON","ADV.P.T.A.RAHIM","ASHRAFALI KALIYATH","PROFESSOR.M.THOMAS MATHEW","K.V. SANKARANARAYANAN","ADV. V.V. PRAKASH","DR. SEBASTIAN PAUL",
                                                    "PROF. JOSEPH AUGUSTINE","ADV MOHAN THOMAS","CHERIYAN PHILIP","ADV. M.V.JAYADALI")~"LDF",
                                   party %in% c("BJP","RSPK(B)" ) ~"NDA",
                 TRUE ~ "OTHERS"))

#kl_11 %>% filter( grepl("kattak",constituency_name ,ignore.case =TRUE))


###16


kl_16<- ae_kl %>% filter(year %in% c(2016) & poll_no ==0 & party != "NOTA")

#unique(kl_16$party[kl_16$position==1])





kl_16 <- kl_16 %>% mutate(front = case_when(party %in% c("INC", "KEC(M)","SJD", "IMUL" ,"JD(U)","CMPKSC","RSP") ~"UDF",
                                   party %in% c("CPI","CPM","JD(S)","NCP", "INL","C(S)","KEC(B)","NSC") ~"LDF",
                                   
                                   candidate %in% c("ADV. P.T.A. RAHIM","KARAT RAZACK","K.P. BEERANKUTTY","P V ANVAR","V ABDURAHIMAN","GAFOOR P LILLIS","DR. K.T. JALEEL","ADV. ROY VARICATTU","KOVOOR KUNJUMON","ADV.ANTONY RAJU")~"LDF",
                                   party %in% c("BJP","BDJS" ) ~"NDA",
                 TRUE ~ "OTHERS"))

# kl_16 %>% filter( grepl("thodupuzha",constituency_name ,ignore.case =TRUE))
# 
# 
# kl_16 %>% filter( grepl("antony",candidate ,ignore.case =TRUE))
# 
# kl_16 %>% filter(party =="RSP")

kl_11_16 <- rbindlist(list(kl_11,kl_16), use.names = TRUE)


kl_el <- rbindlist(list(kl_14_19, kl_11_16), use.names = TRUE, fill = TRUE)

```
# Front

## vote share


```{r}


vs_front <- read.csv("D:/cpr/elections/kerala/vote.csv")


names(vs_front)[1] <- "year"

ggplot(vs_front, aes(factor(year), vs, fill = front, group = front, label = round(vs,0)))+
  geom_bar(stat= "identity", position = "stack")+
  geom_text(position= position_stack(vjust = .5))+
  #   geom_line(size =1)+
  # geom_point(color = "black")+
  scale_fill_manual(values = c(
                                "UDF" = "steelblue",
                                "LDF" = "red",
                             
                                "NDA" = "darkorange1"))+
labs(title = "Vote share of major fronts",subtitle = "1996:2019",  x = "Years", y = "Vote share (%)", fill = "Election Type" )+

  theme_minimal()+
  
  theme(plot.margin = unit(c(.5,.5,.5,.5), "cm"),
        #legend.position = "bottom",
        plot.background = element_blank(),
        plot.title = element_text( size = 18, family = "serif"),
        plot.subtitle = element_text( size = 15,color = "grey50",
                                     margin = margin(t = 0, r = 0, b = 20, l = 0)),
        text = element_text(color = "gray20",family = "serif"),
        axis.text.x = element_text( 
                                   hjust = .5, vjust = 0),
        legend.title = element_blank(),
        legend.text = element_text(size = 12),
        axis.text = element_text(face = "italic", size = 10),
        axis.title = element_text(vjust = -1, size = 15),        
        axis.ticks = element_blank(),
        panel.grid.major = element_line(color = "gray50", size = .5),
        panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
         axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
       # axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        axis.line.x = element_line(),
        axis.title.x = element_blank()
  ) 
  

```

---

## seat share

```{r}
seats_front <- read.csv("D:/cpr/elections/kerala/assembly_seg.csv")


names(seats_front)[1] <- "year"

ggplot(seats_front, aes(factor(year), seats, fill = front, group = front, label = ifelse(seats>0,seats, NA)))+
  geom_bar(stat= "identity", position = "fill")+
  geom_text(position= position_fill(vjust = .5))+
  scale_fill_manual(values = c(
                                "UDF" = "steelblue",
                                "LDF" = "red",
                             
                                "NDA" = "darkorange1"))+
labs(title = "Seat share of major fronts",subtitle = "Assembly segements - 1996:2019",  x = "Years", y = "Vote share (%)", fill = "Election Type" )+

  theme_minimal()+
  
  theme(plot.margin = unit(c(.5,.5,.5,.5), "cm"),
        #legend.position = "bottom",
        plot.background = element_blank(),
        plot.title = element_text( size = 18, family = "serif"),
        plot.subtitle = element_text( size = 15,color = "grey50",
                                     margin = margin(t = 0, r = 0, b = 20, l = 0)),
        text = element_text(color = "gray20",family = "serif"),
        axis.text.x = element_text( 
                                   hjust = .5, vjust = 0),
        legend.title = element_blank(),
        legend.text = element_text(size = 12),
        axis.text = element_text(face = "italic", size = 10),
        axis.title = element_text(vjust = -1, size = 15),        
        axis.ticks = element_blank(),
        panel.grid.major = element_line(color = "gray50", size = .5),
        panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
         axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
       # axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        axis.line.x = element_line(),
        axis.title.x = element_blank()
  ) 
```



# SC/ST


```{r}


shrug_cen <- read.csv("D:/cpr/elections/kerala/data/shrug_cen_kl.csv")

shrug_cen$ac_no <- as.numeric(str_sub(shrug_cen$ï..ac08_id,-3))

kl_vs_11 <- kl_el %>% filter(front %in% c("LDF", "UDF") & year == 2011) %>% select(year,constituency_no,party,front, vote_share_percentage) %>% rename(vs_11 = vote_share_percentage)

kl_vs_16 <- kl_el %>% filter(front%in% c("LDF", "UDF") & year == 2016) %>% select(year,constituency_no,party,front, vote_share_percentage) %>% rename(vs_16 = vote_share_percentage)

kl_vs_11_16 <- inner_join(kl_vs_16 , kl_vs_11, by = c("constituency_no", "party"))

kl_vs_11_16 $vs_change <- kl_vs_11_16$vs_16- kl_vs_11_16$vs_11

shrug_sc <- shrug_cen %>% select(ac_no, sc_pc, st_pc) %>% mutate(sc_st_pc = sc_pc +st_pc)

## left_congress




#####

kl_sc<- dplyr::inner_join(kl_vs_11_16, shrug_sc, by = c("constituency_no" = "ac_no"))


kl_el_sc <- inner_join(kl_el,shrug_sc, by = c("constituency_no" = "ac_no"))


```


```{r}
ggplot(kl_el_sc %>% filter(front %in% c("UDF","LDF")), aes(sc_st_pc,vote_share_percentage , color = front))+
  geom_point(alpha = .5)+
  geom_smooth(se = FALSE, method = "lm")+
    scale_color_manual(values = c("LDF" = "red",
                              
                                
                                "UDF" = "steelblue")) +
     labs(title = "Front vote share as a function of SC&ST constituents ", y = "Vote share(%)",subtitle = "WB GE elections - 1996:2019", x = "SC&ST (%) Rural", color = "Party")+
    theme_minimal()+
  theme(plot.margin = unit(c(.5,.5,.5,.5), "cm"),
        #legend.position = "bottom",
        plot.background = element_blank(),
        plot.title = element_text( size = 18, family = "serif"),
        plot.subtitle = element_text( size = 15,color = "grey50",
                                     margin = margin(t = 0, r = 0, b = 20, l = 0)),
        text = element_text(color = "gray20",family = "serif"),
        axis.text.x = element_text( 
                                   hjust = .5, vjust = 0),
        legend.title = element_blank(),
        legend.text = element_text(size = 12),
        axis.text = element_text(face = "italic", size = 10),
        axis.title = element_text(vjust = -1, size = 15),        
        axis.ticks = element_blank(),
        panel.grid.major = element_line(color = "gray", size = .5),
        panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
         axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
       axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        axis.line.x = element_line(),
        #axis.title.x = element_blank()
  ) +
   lims(x = c(0,40), y= c(0,80))

```


# women turnout



```{r}



ge <- fread("D:/cpr/data/tcpd/TCPD_GE_all.csv")

kl_to <- read.csv("D:/cpr/elections/kerala/data/kl_fe_to.csv")

names(kl_to) <- tolower(names(kl_to))

ge <- fread("D:/cpr/data/tcpd/TCPD_GE_all.csv")

ge_kl <- ge %>% filter(State_Name == "Kerala")

names(ge_kl) <- tolower(names(ge_kl))


ge_kl_to <- inner_join(kl_to, ge_kl, by = c("constituency_no", "year"))

# ge_kl_to <- ge_kl_to  %>% mutate(front = case_when(party %in% c("CPM", "CPI", "RSP", "AIFB") ~"LF",
#                                                 
#                                    TRUE ~party))


ge_kl_to <- ge_kl_to %>% mutate(front= case_when (party %in% c("KEC(M)","KEC(J)",  "INC", "IUML", "MUL","KCM","RSP")  ~"UDF",
                    party %in% c("CPI", "CPM")  ~"LDF",
                    party %in% c("BJP","JD(U)","IFDP")  ~"NDA",
                    TRUE ~party
                    ))

ggplot(ge_kl_to %>% filter(front %in% c("LDF","UDF","NDA")), aes(female_turnout, vote_share_percentage, color = front))+
  geom_point(alpha=0.5)+
  geom_smooth(method = "lm",se = FALSE)+
      scale_color_manual(values = c("LDF" = "red",
                              
                                
                                "UDF" = "steelblue",
                                "NDA" = "darkorange1"))+

   labs(title = "Female turnout as a function of party vote share", y = "Vote share(%)",subtitle = "Kerala GE elections - 1996:2014", x = "Turnout (%)", color = "Party")+
    theme_minimal()+
  theme(plot.margin = unit(c(.5,.5,.5,.5), "cm"),
        #legend.position = "bottom",
        plot.background = element_blank(),
        plot.title = element_text( size = 18, family = "serif"),
        plot.subtitle = element_text( size = 15,color = "grey50",
                                     margin = margin(t = 0, r = 0, b = 20, l = 0)),
        text = element_text(color = "gray20",family = "serif"),
        axis.text.x = element_text( 
                                   hjust = .5, vjust = 0),
        legend.title = element_blank(),
        legend.text = element_text(size = 12),
        axis.text = element_text(face = "italic", size = 10),
        axis.title = element_text(vjust = -1, size = 15),        
        axis.ticks = element_blank(),
        panel.grid.major = element_line(color = "gray", size = .5),
        panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
         axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
       axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        axis.line.x = element_line(),
        #axis.title.x = element_blank()
  ) +
  lims(x = c(55,85), y= c(0,60))
ggsave("D:/cpr/elections/wb/ge_f_to.png", width = 6, height = 4)

```


## region


```{r}

# 
# ge_kl %>% filter(year ==2019 & position ==1) %>% tally(sub_region)

```




