---
title: "Quality of candidates"
author: ""
date: "2020-07-23"
params:
  orig_date: "Original Publish Date: 23 July, 2020"
  update_date: !r paste("Updated on:", format(Sys.time(), '%d %B, %Y'))
output:
  html_document:
    theme: readable
    toc: TRUE
    toc_float: TRUE
    toc_depth: 5
    number_sections: false
    fig_width: 6            
editor_options: 
  chunk_output_type: inline

---

### Document History

`r params$orig_date`

`r params$update_date`

---


```{r set up, warning=FALSE, include=FALSE, message= FALSE}

knitr::opts_chunk$set(cache = FALSE,echo = FALSE, message=FALSE, warning = FALSE, fig.width = 16/2, fig.height = 9/2)


library(tidyverse)
library(data.table)
library(knitr)
library(kableExtra)
library(scales)
library(gridExtra)
library(stargazer)
library(ggbump)


`%!in%` = Negate(`%in%`)

select <- dplyr::select
```


In this post, we are trying to assess nature of candidates in dynast constituency and how it differs from a non-dynast constituency. In the analysis we exclude of the winner since our intention is to asses how having  important dynast candidate affect the general candidate characteristics in that particular constituency. 

# UP

## AE 2012 & 2017 {.tabset}




```{r adr}

## reading adr candidate level data scraped Jatin, includes information for all the candidates for the years 2009,2012,2014,2017,2019


adr <- read.csv( "D:/cpr/UP/up-dynasties/dyn_other_data/adr_candidatelevel.csv")

names(adr)[1] <- "position"

names(adr) <- tolower(names(adr))

adr <- adr %>% dplyr::select( -c(constituency_id,state,         assembly_no,
  month,              poll_no,
  delimid,            position,
  candidate,          sex,
  party,              votes,
  candidate_type,     valid_votes,
  electors,           constituency_name,
  constituency_type,  sub_region,
  n_cand,             turnout_percentage,
  vote_share_percentage,     deposit_lost,
  margin,             margin_percentage,

  enop,
  pid,                max_poll_no,
  last_poll,          contested,
  last_party,         last_constituency_name,
  same_constituency,  same_party,
  no_terms,           turncoat,
  incumbent,          recontest )  )



adr <- adr %>% rename( position = position_tcpd)


##merging the canidate information to the the data frame produced earlier to retrieve if there was dynst winner or runner-up.


dyn <- fread("D:/cpr/UP/up-dynasties/dyn_other_data/dyn_all.csv")

dyn_ae_ge <- dyn %>% filter(election_type %in% c("AE","GE"))

adr_dyn<- merge(adr,dyn_ae_ge, by = c("year", "constituency_no"), all.x = TRUE, allow.cartesian =TRUE)


names(adr_dyn ) <- make.unique(names(adr_dyn ))

adr_dyn$total_assets <- as.numeric(adr_dyn$total_assets)



adr_dyn <- adr_dyn %>% group_by(election_type, year, constituency_no)%>% mutate(dyn_con = ifelse(sum(dyn_cum_2)>=1,TRUE,FALSE))

```





```{r ae level}

adr_dyn_12_17 <- adr_dyn %>% filter (year %in% c(2012,2017))

adr_dyn_09_19 <- adr_dyn %>% filter (year %in% c(2009,2014,2019))

#names(adr_dyn_12_17)

```

### Assets

Constituency type : 1 - Dynast constituency, 2- Non-dynast constituency


```{r}

adr_dyn_12_17 %>% group_by(dyn_con) %>% filter(winner ==0) %>% summarise(mean(total_assets, na.rm =TRUE), mean(total_movable_assets_totals), mean(total_immovable_assets_totals)) %>% kable(caption = "Assets", col.names= c("Dynast constituency ", "Total assets", "Total movable assets", "Total immovable assets")) %>% kable_styling(bootstrap_options = "striped")

```



### Criminality

```{r}


adr_dyn_12_17%>% group_by(dyn_con) %>% filter(winner ==0) %>% summarise(mean(serious_crime), mean(non_serious_crime)) %>% kable(caption = "Criminality", col.names= c("Dynast constituency", "Serious crime", "Non-serious crime"), digits = 2)%>% kable_styling(bootstrap_options = "striped")

```




### Profession

```{r proession, fig.width = 16/2, fig.height = 9/2}



adr_12_17 <- read.csv( "D:/cpr/UP/up-dynasties/dyn_other_data/dyn_adr_12_17.csv")

adr_12_17 <- adr_12_17 %>% mutate(profession_new = ifelse(Profession %in% c("Medical Worker/Doctor","Engineer", "Government Job","Private Job", "Retired", "Journalist") , "Professional Job",
                                             ifelse(Profession %in% c("Social Worker", "Politician"), "Social Work",
                                                    ifelse(Profession %in% c("Dependent", "Driver", "Not Known", "Others", "Wage Labourer/Worker"), "Others", Profession))))

#table(adr_12_17$profession_new)

adr_12_17 %>% group_by(dyn_con, profession_new) %>% filter(winner ==0) %>% summarise(count = n()) %>% group_by(dyn_con) %>% mutate(sum = sum(count), prop = count/sum) %>% select(dyn_con, profession_new, prop) %>%
  ggplot(aes(factor(dyn_con), prop, fill= profession_new,label = round(prop,2)))+
  geom_bar(position = "stack", stat = "identity")+
   geom_text(size = 3, position = position_stack(vjust = 0.5))+
    theme_minimal()+
  scale_x_discrete(labels=(c( "Dynast \n Constituency", "Non - dynast\n  Constituency")))+
  labs(title = " Composition of candidate's professions \n wrt constituency type" ,subtitle = "AE 2012 & 2017",x = "", y = "Proportion", fill = "") +
  coord_fixed(ratio =4)+
    colorspace::scale_fill_discrete_qualitative(palette= "dark3" )+
    theme_minimal()+
  theme(plot.margin = unit(c(.5,.5,.5,.5), "cm"))+
  theme(plot.background = element_blank(),
        axis.line.x = element_line(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.y = element_blank()
  ) 
```


### Education

```{r}

  adr_12_17$education_cl <- case_when(str_detect(adr_12_17$education, "(Pass)| (Others) | (Literate) | (Illiterate)") ~ "School", str_detect(adr_12_17$education,"(Doctorate)|(Post)") ~ "PG+",str_detect(adr_12_17$education,"(Unknown)|(Not Given)") ~"NA" ,TRUE ~ "UG")

#table(adr_12_17$education_cl)

adr_12_17$education_cl <- factor(adr_12_17$education_cl,levels =c( "School", "UG", "PG+"))



adr_12_17 %>% filter(education_cl != "NA"& winner ==0) %>%  group_by(dyn_con, education_cl) %>% summarise(count = n()) %>% group_by(dyn_con) %>% mutate(sum = sum(count), prop = count/sum) %>% arrange(education_cl) %>% select(dyn_con, education_cl, prop) %>% kable(caption = "Education", col.names= c("Constituency type", "Education", "Proportion"), digits = 2)%>% kable_styling(bootstrap_options = "striped")

```



## UP GE 2009:2019 {.tabset}



### Assets




```{r}

adr_dyn_09_19 %>% group_by(dyn_con) %>% filter(winner ==0) %>% summarise(mean(total_assets, na.rm =TRUE), mean(total_movable_assets_totals), mean(total_immovable_assets_totals)) %>% kable(caption = "Assets", col.names= c("Dynast constituency ", "Total assets", "Total movable assets", "Total immovable assets")) %>% kable_styling(bootstrap_options = "striped")

```



### Criminality

```{r}


adr_dyn_09_19%>% group_by(dyn_con) %>% filter(winner ==0) %>% summarise(mean(serious_crime), mean(non_serious_crime)) %>% kable(caption = "Criminality", col.names= c("Dynast constituency", "Serious crime", "Non-serious crime"), digits = 2)%>% kable_styling(bootstrap_options = "striped")

```




<!-- ## GE 2019 -->


<!-- Constituency type : 1 - Dynast constituency, 2- Non-dynast constituency -->


<!-- ```{r file config} -->



<!-- ge_19 <- read.csv("D:/cpr/UP/up-dynasties/dyn_other_data/TCPD_2019_all_candidates_with_caste_and_political_family.csv") -->

<!-- # ge_19 <- read.csv("D:/cpr/UP/up-dynasties/dyn_other_data/tcpd_ge_09_14_19_dyn.csv") -->
<!-- names(ge_19)[1] <- "State_Name" -->

<!-- names(ge_19 ) <- tolower(names(ge_19)) -->



<!-- ge_19 <- ge_19 %>% filter(state_name == "Uttar_Pradesh") -->

<!-- dyn <- read.csv( "D:/cpr/UP/up-dynasties/dyn_other_data/dyn_all.csv") -->

<!-- dyn_ae_ge <- dyn %>% filter(election_type %in% c("AE", "GE")) -->

<!-- ## checks if there was a dynast candidate in that constituency in a particular year -->

<!-- dyn_ae_ge <- dyn_ae_ge  %>% group_by(year,constituency_no) %>% mutate(dyn_con= if_else(any(dyn_cum_2 ==1),1,0)) -->

<!-- dyn_ae_con <- dyn_ae_ge %>% filter(year %in% c(2012,2017)) %>% distinct(constituency_no,year, .keep_all = TRUE)%>% select(year, constituency_name, constituency_no, dyn_con) %>% arrange( constituency_no, year) -->


<!-- ## create a data frame which tells you if there was a dynast canidate in the top two positions. -->

<!-- # dyn_ae_ge_uniq_con <- dyn_ae_ge %>% select(year, constituency_no, dyn_con, dyn_cum_2)%>% distinct(year, constituency_no, .keep_all = TRUE) -->

<!-- dyn_ge19 <- merge(ge_19, dyn_ae_ge , by = c("year", "constituency_no"), all.x = TRUE, allow.cartesian =TRUE) -->

<!-- dyn_ge19  <- dyn_ge19 %>% filter(dyn_cum_2 ==0) -->

<!-- ``` -->


<!-- ### Assets -->

<!-- ```{r} -->

<!-- dyn_ge19 %>% group_by(dyn_con) %>% summarise(mean(myneta_assets, na.rm = TRUE), mean(myneta_liabilities, na.rm =TRUE), mean(myneta_net_assets, na.rm =TRUE)) %>% kable(caption = "Assets", col.names= c("Constituency Type", "Assets", "Total liabilities", "Net assets"), digitis = 0)%>% kable_styling(bootstrap_options = "striped") -->


<!-- ``` -->


<!-- ### Criminality -->

<!-- ```{r} -->
<!-- dyn_ge19 %>% group_by(dyn_con) %>% summarise(mean(myneta_criminal_cases, na.rm =TRUE), mean(myneta_serious_criminal_cases, na.rm =TRUE)) %>% kable(caption = "Criminality", col.names= c("Constituency Type", "criminal cases - count", "Serious crime - logical"), digits = 2)%>% kable_styling(bootstrap_options = "striped") -->


<!-- ``` -->


<!-- ###  Gender -->


<!-- ```{r} -->
<!-- dyn_ge19 %>% filter(myneta_gender!= "") %>% group_by(dyn_con, myneta_gender) %>% summarise(count = n()) %>% group_by(dyn_con) %>% mutate(sum = sum(count), prop = count/sum) %>% select(dyn_con, myneta_gender, prop) %>% kable(caption = "Gender", col.names= c("Constituency type", "Gender", "Proportion"), digits = 2)%>% kable_styling(bootstrap_options = "striped") -->

<!-- ``` -->

<!-- ### Education -->

<!-- ```{r} -->
<!-- #table(dyn_ge19$myneta_education) -->

<!--   dyn_ge19$education <- case_when(str_detect(dyn_ge19$myneta_education, "(Pass)| (Others) | (Literate) | (Illiterate)") ~ "School", str_detect(dyn_ge19$myneta_education,"(Doctorate)|(Post)") ~ "PG+", TRUE ~ "UG") -->

<!-- dyn_ge19$education <- factor(dyn_ge19$education,levels =c( "School", "UG", "PG+")) -->



<!-- dyn_ge19 %>% filter(myneta_education!= "") %>% group_by(dyn_con, education) %>% summarise(count = n()) %>% group_by(dyn_con) %>% mutate(sum = sum(count), prop = count/sum) %>%arrange(education) %>% select(dyn_con, education, prop) %>% kable(caption = "Education", col.names= c("Constituency type", "Education", "Proportion"), digits = 2)%>% kable_styling(bootstrap_options = "striped") -->



<!-- ``` -->

<!-- ### Professsion -->

<!-- ```{r} -->

<!-- profession <- data.frame(table(dyn_ge19$myneta_profession)) %>% arrange(-Freq) -->

<!-- # write.csv(profession,"D:/cpr/up-dynasties/dyn_other_data/profession.csv" ) -->
<!-- # table(dyn_ge19$profession) -->

<!-- agri <- c("^Agriculture","Agriculture", "^Farmer", "Farming") -->

<!-- retired <- c("Pension", "retire", "retired", "Pensioner") -->

<!-- social <- c("^Social", "Social work", "Social Work") -->

<!-- teaching <-   c("Teacher", "Teaching", "College", "School", "Lecturer", "Lecture", "Tution") -->





<!--   dyn_ge19$profession <- case_when(str_detect(dyn_ge19$myneta_profession, paste(agri, collapse = "|")) ~ "Agriculture", -->
<!--                                    str_detect(dyn_ge19$myneta_profession, "Advocate")~"Advocate", -->
<!--                                    str_detect(dyn_ge19$myneta_profession, paste(teaching, collapse = "|"))~"Teaching", -->
<!--                                    str_detect(dyn_ge19$myneta_profession, paste(social, collapse = "|"))~"Social Worker", -->
<!--                                    str_detect(dyn_ge19$myneta_profession, paste(retired, collapse = "|"))~"Retired", -->
<!--                                    str_detect(dyn_ge19$myneta_profession, "^Business")~"Business", -->
<!--                                    str_detect(dyn_ge19$myneta_profession, "Doctor")~"Doctor", -->
<!--                                    TRUE ~ "Others") -->

<!--   dyn_ge19 %>% group_by(dyn_con, profession) %>% summarise(count = n()) %>% group_by(dyn_con) %>% mutate(sum = sum(count), prop = count/sum) %>% select(dyn_con, profession,  prop) %>% -->
<!--      ggplot(aes(factor(dyn_con), prop, fill= profession,label =round(prop*100)))+ -->
<!--   geom_bar(position = "stack", stat = "identity")+ -->
<!--    geom_text(size = 2, position = position_stack(vjust = 0.5))+ -->
<!--     theme_minimal()+ -->
<!--   scale_x_discrete(labels=(c( "Dynast \n Constituency", "Non - dynast \n Constituency")))+ -->
<!--   labs(title = " Composition of candidate's professions \n wrt constituency type" ,subtitle = "AE 2012 & 2017",x = "", y = "", fill = "") + -->
<!--   coord_fixed(ratio =3)+ -->
<!--     colorspace::scale_fill_discrete_qualitative(palette= "dark3" )+ -->
<!--     theme_minimal()+ -->
<!--   theme(plot.margin = unit(c(.5,.5,.5,.5), "cm"))+ -->
<!--   theme(plot.background = element_blank(), -->
<!--         axis.line.x = element_line(), -->
<!--         panel.grid.major = element_blank(), -->
<!--         panel.grid.minor = element_blank(), -->
<!--         axis.text.y = element_blank() -->
<!--   )  -->


<!-- ``` -->



<!-- # India -->


<!-- ## GE 2009 &19 {.tabset} -->

<!-- Constituency type : 1 - Dynast constituency, 2- Non-dynast constituency -->

<!-- ```{r} -->
<!-- dyn_ge <-fread("D:/cpr/UP/up-dynasties/dyn_other_data/tcpd_ge_09_14_19_dyn.csv") -->



<!-- names(dyn_ge)[1] <- "State_Name" -->

<!-- names(dyn_ge) <- tolower(names(dyn_ge)) -->

<!-- dyn_ge$dynast <- ifelse(dyn_ge$dyn==1,1,0) -->

<!-- adr_ge <- read.csv("D:/cpr/UP/up-dynasties/dyn_other_data/adr/adr_tcpd_09_14_19.csv") -->

<!-- #names(adr_ge) -->

<!-- #adr_ge<- adr_ge %>% select(2:10,55:61, State_Name, Year,Constituency_No, Position) -->

<!-- names(adr_ge) <- tolower(names(adr_ge)) -->

<!-- #ge_cen$Age <- NULL -->


<!-- adr_ge$state_name <- tolower(adr_ge$state_name ) -->

<!-- dyn_ge$state_name <- tolower(dyn_ge$state_name) -->

<!-- dyn_ge <- dyn_ge %>% select(-c(pid, party, sex, candidate,constituency_name,constituency_type, vote_share_percentage)) -->

<!-- dyn_adr_ge <- merge(dyn_ge,adr_ge, by = c("state_name","year", "constituency_no", "position")) -->

<!-- #ge_cen_adr <- ge_cen_adr %>% filter(total_assets>0) -->
<!-- #  -->
<!-- # names(dyn_adr_ge) <- tolower(names(dyn_adr_ge)) -->

<!-- dyn_adr_ge<- dyn_adr_ge%>% group_by(year,constituency_no) %>% mutate(dyn_con= if_else(any(dyn ==1),1,0)) -->


<!-- #write.csv(dyn_adr_ge, "D:/cpr/data/adr/dyn_adr_ge.csv" ) -->


<!-- ``` -->




<!-- ```{r} -->

<!-- dyn_con <- dyn_adr_ge %>% group_by(year,state_name, constituency_no) %>% summarise(dyn_contest = ifelse(sum(dyn)>0,1,0)) -->

<!-- dyn_adr_ge <- right_join(adr_ge,dyn_con, by = c("state_name","year", "constituency_no")) -->

<!-- dyn_adr_ge$gender <- ifelse(dyn_adr_ge$sex=="M","M","F") -->



<!-- dyn_adr_ge$reservation<- ifelse(dyn_adr_ge$constituency_type=="GEN","GEN","SC/ST") -->


<!-- # library(fixest) -->
<!-- # etable(feglm(dyn_contest~log(as.numeric(total_assets))+turnout_percentage+serious_crime+non_serious_crime+position+n_cand+no_terms+incumbent+relevel(as.factor(gender), ref = "M")+reservation|state_name +year, data = dyn_adr_ge,family = binomial(link = "probit") ) ) %>%  -->
<!-- #   kable() -->


<!-- ``` -->


<!-- ## conlevle -->

<!-- ###onstinous model -->

<!-- ```{r} -->



<!-- ##education -->



<!-- adr_ge <- adr_ge %>% mutate(edu_yrs = case_when( -->
<!--   education == "Doctorate" ~ "22", -->
<!--   education =="Post Graduate" ~"17", -->
<!--   education =="Graduate Professional" ~"16", -->
<!--   education == "Graduate" ~"15", -->
<!--   education =="12th Pass" ~"12", -->
<!--   education =="10th Pass" ~"10", -->
<!--   education == "8th Pass" ~"8", -->
<!--   education =="5th Pass" ~"5", -->
<!--   education %in% c("Literate", "Unknown", "Not Given") ~"2", -->
<!--   education =="Illiterate" ~"0", -->
<!--   education== "Others" ~"5", -->
<!--   TRUE ~"NAN" -->
<!--   )) -->
<!-- adr_ge$edu_yrs <- as.numeric(adr_ge$edu_yrs) -->
<!-- #  -->
<!-- #  "Graduate Professional" "Graduate"              -->
<!-- #  "12th Pass"             "10th Pass"             -->
<!-- # "8th Pass"              "Post Graduate"         -->
<!-- #  "Doctorate"             "Others"                -->
<!-- #  "5th Pass"              "Illiterate"            -->
<!-- # "Literate"              "Not Given"             -->
<!-- #  "Unknown"  -->




<!-- # dyn_con <- dyn_adr_ge %>% group_by(year,state_name, constituency_no) %>% summarise(dyn_contest = ifelse(sum(dyn)>0,1,0)) -->


<!-- adr_ge$gender <- ifelse(adr_ge$sex=="M",1,0) -->


<!-- dyn_adr_ge$reservation<- ifelse(dyn_adr_ge$constituency_type=="GEN","GEN","SC/ST") -->

<!-- adr_ge_reg <- adr_ge %>% group_by(year, state_name, constituency_no) %>% mutate(mean_edu = mean(edu_yrs, na.rm = TRUE), median_assets = median(as.numeric(total_assets, na.rm = TRUE)), mean_male = mean(gender, na.rm = TRUE), mean_serious_crime = mean(serious_crime, na.rm = TRUE),mean_non_serious_crime = mean(non_serious_crime, na.rm = TRUE)) %>% distinct(year, state_name, constituency_no ,.keep_all= TRUE) -->



<!-- dyn_con <- dyn_ge %>% group_by(year,state_name, constituency_no) %>% summarise(dyn_contest = ifelse(sum(dyn)>0,1,0)) -->

<!-- adr_ge_reg <-  right_join(adr_ge_reg,dyn_con, by = c("state_name","year", "constituency_no")) -->

<!-- adr_ge_reg$reservation<- ifelse(adr_ge_reg$constituency_type=="GEN","GEN","SC/ST") -->




<!-- library(lfe) -->

<!-- ## mean_edu -->


<!-- summary(felm(mean_edu ~dyn_contest+turnout_percentage+median_assets+mean_male+mean_serious_crime+mean_non_serious_crime+reservation+enop|state_name +year, data =adr_ge_reg )) -->


<!-- ## dynast contestant -->

<!-- summary(felm(dyn_contest ~mean_edu+turnout_percentage+median_assets+mean_male+mean_serious_crime+mean_non_serious_crime+reservation+enop|state_name +year, data =adr_ge_reg )) -->

<!-- ``` -->
<!-- ### binary model -->


<!-- ```{r} -->



<!-- adr_ge_reg <- adr_ge %>% group_by(year, state_name, constituency_no) %>%mutate(mean_edu = mean(edu_yrs, na.rm = TRUE), prop_edu = sum(edu_yrs>mean_edu)/n_cand,  median_assets = median(as.numeric(total_assets, na.rm = TRUE)), prop_assets = sum(total_assets>median_assets)/n_cand, prop_male = mean(gender, na.rm = TRUE), prop_serious_crime= sum(serious_crime>0)/n_cand, prop_non_serious_crime = sum(non_serious_crime>0)/n_cand)   %>% distinct(year, state_name, constituency_no ,.keep_all= TRUE) -->


<!-- dyn_con <- dyn_ge %>% group_by(year,state_name, constituency_no) %>% summarise(dyn_contest = ifelse(sum(dyn)>0,1,0)) -->

<!-- adr_ge_reg <-  right_join(adr_ge_reg,dyn_con, by = c("state_name","year", "constituency_no")) -->

<!-- adr_ge_reg$reservation<- ifelse(adr_ge_reg$constituency_type=="GEN","GEN","SC/ST") -->


<!-- ## census -->

<!-- cen <- read.csv("D:/cpr/data/census/pc_2011_census.csv") -->


<!-- cen$st_name <- tolower(cen$st_name) -->

<!-- adr_ge_reg <- inner_join(adr_ge_reg, cen, by = c("state_name"= "st_name", "constituency_no"="pc_code")) -->


<!-- ## education -->


<!-- summary(felm(prop_edu~dyn_contest+prop_assets+prop_male+prop_serious_crime+turnout_percentage+enop+reservation+WEALTHSCORE|state_name +year, data = adr_ge_reg )) -->


<!-- ## assets -->


<!-- summary(felm(prop_assets~prop_edu+dyn_contest+prop_male+prop_serious_crime+turnout_percentage+enop+reservation|state_name +year, data = adr_ge_reg )) -->


<!-- ## serious crime -->

<!-- summary(felm(prop_serious_crime~prop_edu+dyn_contest+prop_male+prop_assets+turnout_percentage+enop+reservation|state_name +year, data = adr_ge_reg )) -->


<!-- ## dynast contestant -->

<!-- summary(felm(dyn_contest~prop_serious_crime+prop_edu+prop_male+prop_assets+turnout_percentage+enop+reservation|state_name +year, data = adr_ge_reg )) -->

<!-- # dyn_ae_ge %>% group_by(election_type, dyn_cum_2, position) %>% summarise(count=n()) %>%ungroup()%>% select(election_type, dyn_cum_2,position, count) %>% pivot_wider(names_from = c(election_type, position), values_from = count) %>% kable() %>% kable_styling(full_width = F) -->




<!-- ``` -->




<!-- ### Assets -->

<!-- ```{r} -->

<!-- dyn_adr_ge$total_liabilities <- as.numeric(dyn_adr_ge$total_liabilities) -->

<!-- dyn_adr_ge$total_assets <- as.numeric(dyn_adr_ge$total_assets) -->

<!-- dyn_adr_ge %>%filter(dyn!=1) %>% group_by(dyn_con) %>% summarise(mean(total_assets, na.rm = TRUE), mean(total_liabilities, na.rm =TRUE)) %>% kable(caption = "Assets", col.names= c("Constituency Type", "Assets", "Total liabilities"), digitis = 0)%>% kable_styling(bootstrap_options = "striped") -->


<!-- ``` -->


<!-- ### Criminality -->

<!-- ```{r} -->
<!-- dyn_adr_ge %>%filter(dyn!=1) %>% group_by(dyn_con) %>% summarise(mean(non_serious_crime, na.rm =TRUE), mean(serious_crime, na.rm =TRUE)) %>% kable(caption = "Criminality", col.names= c("Constituency Type", "Non-serious crime", "Serious crime "), digits = 2)%>% kable_styling(bootstrap_options = "striped") -->


<!-- ``` -->

<!-- ### Education -->

<!-- ```{r} -->
<!-- #table(dyn_ge19$myneta_education) -->

<!--  dyn_adr_ge$education_1 <-  dyn_adr_ge$education -->

<!--   dyn_adr_ge$education <- case_when(str_detect(dyn_adr_ge$education, "(Pass)| (Others) | (Literate) | (Illiterate)") ~ "School", str_detect(dyn_adr_ge$education,"(Doctorate)|(Post)") ~ "PG+", TRUE ~ "UG") -->

<!-- dyn_adr_ge$education <- factor(dyn_adr_ge$education,levels =c( "School", "UG", "PG+")) -->



<!-- dyn_adr_ge %>% filter(education!= "") %>% group_by(dyn_con, education) %>% summarise(count = n()) %>% group_by(dyn_con) %>% mutate(sum = sum(count), prop = count/sum) %>%arrange(education) %>% select(dyn_con, education, prop) %>% kable(caption = "Education", col.names= c("Constituency type", "Education", "Proportion"), digits = 2)%>% kable_styling(bootstrap_options = "striped") -->



<!-- ``` -->


<!-- ## Model -->



<!-- ```{r} -->
<!-- # ge_all <- fread("D:/cpr/data/tcpd/TCPD_GE_all.csv") -->
<!-- #  -->
<!-- # names(ge_all) <- tolower(names(ge_all)) -->
<!-- #  -->
<!-- #  -->
<!-- #  -->
<!-- # merge(dyn_ge, ge_all, by = c("state_name", "constituency_no")) -->

<!-- ``` -->




<!-- ```{r} -->

<!-- names(dyn_adr_ge) -->



<!-- dyn_adr_ge$total_assets <- as.numeric(dyn_adr_ge$total_assets) -->

<!-- dyn_adr_ge %>% filter(is.numeric(total_assets) & !is.nan(total_assets)&!is.na(total_assets))%>% filter(between(total_assets, quantile(total_assets, .05), quantile(total_assets, .95))) %>%  -->
<!--   ggplot(aes(total_assets))+ -->
<!--   geom_histogram()+ -->
<!--   scale_x_continuous(labels = unit_format(unit = "M", scale = 1e-6)) -->

<!-- ``` -->


<!-- # Index{.tabset} -->


<!-- For the candidate with 5 percent vote -->


<!-- ### education -->


<!-- ```{r} -->

<!-- #names(adr_ge) <- tolower(names(adr_ge)) -->

<!-- dyn_adr_ge <- dyn_adr_ge %>% mutate(edu_val = case_when( -->
<!--   education == "Doctorate" ~ "22", -->
<!--   education =="Post Graduate" ~"17", -->
<!--   education =="Graduate Professional" ~"16", -->
<!--   education == "Graduate" ~"15", -->
<!--   education =="12th Pass" ~"12", -->
<!--   education =="10th Pass" ~"10", -->
<!--   education == "8th Pass" ~"8", -->
<!--   education =="5th Pass" ~"5", -->
<!--   education %in% c("Literate", "Unknown", "Not Given") ~"2", -->
<!--   education =="Illiterate" ~"0", -->
<!--   education== "Others" ~"5", -->
<!--   TRUE ~"NAN" -->
<!--   )) -->

<!-- dyn_adr_ge$edu_val <- as.numeric(dyn_adr_ge$edu_val ) -->





<!-- dyn_adr_ge <- dyn_adr_ge %>% group_by(year, state_name,constituency_no) %>% mutate(edu_con = sum(edu_val), n_cand= n(), edu_point = edu_con/(n_cand*22)) %>% select(-c(edu_con, edu_val)) %>% ungroup() -->

<!-- #  -->
<!-- # dyn_adr_ge %>% group_by(year, state_name,constituency_no) %>% summarise(edu = sum(edu_val), count = n(), edu_point = edu/(count*22)) %>%  -->
<!-- #    ggplot(aes(edu_point, fill = state_name))+ -->
<!-- #    geom_density()+ -->
<!-- #   theme(legend.position = "none") -->
<!-- #  -->
<!-- # ## state -->


<!-- # dyn_adr_ge %>% distinct(year, state_name,constituency_no, .keep_all=TRUE) %>%  -->
<!-- #   ggplot(aes(edu_point, fill = state_name))+ -->
<!-- #   geom_density()+ -->
<!-- #   theme(legend.position = "none") -->
<!-- #  -->
<!-- #  -->
<!-- # ## India -->
<!-- #  -->
<!-- #  -->
<!-- #  -->
<!-- # dyn_adr_ge %>% group_by(year, state_name,constituency_no, .keep_all=TRUE) %>%  -->
<!-- #   ggplot(aes(edu_point))+ -->
<!-- #   geom_histogram(fill =" steelblue") -->
<!-- #   theme_minimal() -->

<!-- ``` -->

<!-- ### Dynasticism -->


<!-- ```{r} -->

<!-- dyn_adr_ge <- dyn_adr_ge %>% group_by(state_name, year, constituency_no) %>% mutate(dyn_con = sum(dyn), dyn_point = dyn_con/n_cand)  %>% ungroup() -->


<!-- dyn_adr_ge$dyn_inv <-1- dyn_adr_ge$dyn -->
<!-- ## states -->


<!-- dyn_adr_ge %>% distinct(year, state_name,constituency_no, .keep_all=TRUE) %>%  -->
<!--   ggplot(aes(dyn_point, fill = state_name))+ -->
<!--   geom_density()+ -->
<!--    theme(legend.position = "none") -->


<!-- ## India -->

<!-- dyn_adr_ge %>% distinct(year, state_name,constituency_no, .keep_all=TRUE) %>%  -->
<!--   ggplot(aes(dyn_point))+ -->
<!--   geom_histogram(fill =" steelblue")+ -->
<!--    theme(legend.position = "none")+ -->
<!--   theme_minimal() -->


<!-- ``` -->

<!-- ## Income -->




<!-- ```{r} -->



<!-- library(DescTools) -->


<!-- dyn_adr_ge <- dyn_adr_ge %>%  group_by(year, state_name,constituency_no) %>%  -->
<!--   mutate(gini = Gini(total_assets,na.rm = TRUE)) %>% ungroup() %>% mutate(gini = ifelse(is.na(gini),.9,gini), gini_inv = 1-gini) -->

<!-- ## need to match othe missing ones - what if many others are only one observations? -->
<!-- #  -->
<!-- # dyn_adr_ge %>% filter(state_name=="andhra pradesh" & year ==2009& constituency_no==2) -->
<!-- #  -->
<!-- # dyn_adr_ge %>% distinct(year, state_name,constituency_no, .keep_all=TRUE) %>% filter(n_cand==1) -->
<!-- dyn_adr_ge %>% distinct(year, state_name,constituency_no, .keep_all=TRUE) %>%  -->
<!--   ggplot(aes(gini))+ -->
<!--   geom_histogram(fill =" steelblue")+ -->
<!--    theme(legend.position = "none")+ -->
<!--   theme_minimal() -->

<!-- ``` -->


<!-- ### Criminality -->


<!-- ```{r} -->

<!-- dyn_adr_ge <- dyn_adr_ge %>% mutate(serious_crime_log = ifelse(serious_crime==0,0,1),non_serious_crime_log = ifelse(non_serious_crime==0,0,1)) -->

<!-- dyn_adr_ge <- dyn_adr_ge %>% group_by(state_name, year, constituency_no) %>% mutate(s_crime_con = sum(serious_crime_log), s_crime_point = s_crime_con/n_cand, -->
<!--                                                                                     ns_crime_con = sum(non_serious_crime_log), ns_crime_point = ns_crime_con/n_cand -->
<!--                                                                                     ) %>% select(-c( ns_crime_con, s_crime_con,serious_crime_log,non_serious_crime_log)) %>% ungroup() -->


<!-- dyn_adr_ge <- dyn_adr_ge %>% mutate(ns_crime_inv = 1- ns_crime_point,s_crime_inv = 1- s_crime_point ) -->

<!-- dyn_adr_ge %>% distinct(year, state_name,constituency_no, .keep_all=TRUE) %>%  -->
<!--   ggplot(aes(s_crime_point))+ -->
<!--   geom_histogram(fill =" steelblue", bins=5)+ -->
<!--    theme(legend.position = "none")+ -->
<!--   theme_minimal() -->

<!-- dyn_adr_ge %>% distinct(year, state_name,constituency_no, .keep_all=TRUE) %>%  -->
<!--   ggplot(aes(ns_crime_point))+ -->
<!--   geom_histogram(fill =" steelblue", bins=5)+ -->
<!--    theme(legend.position = "none")+ -->
<!--   theme_minimal() -->
<!-- ``` -->


<!-- <!-- ## Gender --> -->


<!-- <!-- ```{r} --> -->


<!-- <!-- dyn_adr_ge$gender <- ifelse(dyn_adr_ge$sex =="M",1,0) --> -->

<!-- <!-- dyn_adr_ge dyn_adr_ge %>% group_by(state_name, year, constituency_no) %>% mutate(gen_con = sum(gender), male = sum(gen_con)/n_cand) %>% select(-c(gen_con)) %>% ungroup() %>% filter(male>1) --> -->

<!-- <!-- dyn_adr_ge %>% distinct(year, state_name,constituency_no, .keep_all=TRUE) %>%  --> -->
<!-- <!--   ggplot(aes(male))+ --> -->
<!-- <!--   geom_histogram(fill =" steelblue")+ --> -->
<!-- <!--    theme(legend.position = "none")+ --> -->
<!-- <!--   theme_minimal() --> -->

<!-- <!-- c <- dyn_adr_ge %>% group_by(state_name, year, constituency_no) %>% summarise(gen_con = sum(gender), male = sum(gen_con)/n_cand)  --> -->

<!-- <!-- ``` --> -->

<!-- ## final one -->


<!-- - education - 1 means most educated -->

<!-- - gini inversed - 1 means highly diverse -->

<!-- - dynasticism inversed - 1 means no dynasticism -->

<!-- - criminality -->
<!--         - serious inversed - 1 means there is no serious criminals -->
<!--         - non-serious inversed - 1 means there is no non-serious criminals -->


<!-- ```{r} -->

<!-- dyn_adr_ge$div_point <- (dyn_adr_ge$edu_point +dyn_adr_ge$gini_inv + dyn_adr_ge$dyn_inv + dyn_adr_ge$s_crime_inv)/5 -->


<!-- dyn_adr_ge %>% distinct(year, state_name,constituency_no, .keep_all=TRUE) %>%  -->
<!--   ggplot(aes(div_point))+ -->
<!--   geom_histogram() -->
<!-- ``` -->

<!-- ## model -->





<!-- ```{r} -->

<!-- df <- dyn_adr_ge %>% distinct(year, state_name,constituency_no, .keep_all=TRUE) %>% select(gini_inv, edu_point,dyn_inv,s_crime_inv) -->

<!-- cor_df <- cor(df) -->
<!-- library(corrplot) -->

<!-- corrplot(cor_df, method = "circle") -->

<!-- dyn_adr_ge_uniq <- dyn_adr_ge %>% distinct(year, state_name,constituency_no, .keep_all=TRUE) -->

<!-- dyn_adr_ge_uniq$reservation <- ifelse(dyn_adr_ge_uniq$constituency_type =="GEN","GEN","SC/ST") -->
<!-- ``` -->


<!-- ```{r} -->

<!-- dyn_adr_ge_earlier <- dyn_adr_ge_uniq %>%group_by(year, state_name, constituency_no) %>%  mutate(dyn_won_earlier = ifelse(position==1&dyn==1,1,0))%>% filter(year!= 2019)%>%  select(year, state_name, constituency_no, dyn_contest_earlier =dyn_con, dyn_won_earlier) %>% mutate(year_later = ifelse(year==2009, 2014,2019)) -->



<!-- dyn_adr_ge_uniq_reg <- inner_join(dyn_adr_ge_uniq, dyn_adr_ge_earlier, by = c("year", "state_name", "constituency_no")) -->


<!-- dyn_adr_ge_reg <- inner_join(dyn_adr_ge_uniq, dyn_adr_ge_earlier, by = c("year", "state_name", "constituency_no")) -->

<!-- ``` -->



<!-- ## All index -->


<!-- ```{r} -->


<!-- library(lfe) -->

<!-- dyn_adr_ge_uniq_reg$dynast_contest <- ifelse(dyn_adr_ge_uniq_reg$dyn_con>0,1,0) -->

<!-- summary(felm( turnout_percentage~ reservation+n_cand+dynast_contest|factor(year)+factor(state_name), data =dyn_adr_ge_uniq_reg )) -->

<!-- ``` -->
<!-- ## Dynasticim -->

<!-- ```{r} -->

<!-- summary(felm( dyn_inv~turnout_percentage + reservation+n_cand+dyn_won_earlier|factor(year)+factor(state_name), data =dyn_adr_ge_uniq_reg )) -->


<!-- ``` -->
<!-- ### gini -->

<!-- ```{r} -->

<!-- summary(felm( gini_inv~turnout_percentage + reservation+n_cand+dyn_won_earlier|factor(year)+factor(state_name), data =dyn_adr_ge_uniq_reg )) -->



<!-- ``` -->

<!-- ### education -->

<!-- ```{r} -->
<!-- summary(felm( edu_point~turnout_percentage + reservation+n_cand+dyn_won_earlier|factor(year)+factor(state_name), data =dyn_adr_ge_uniq_reg )) -->
<!-- ``` -->

<!-- ### criminality -->

<!-- ```{r} -->

<!-- summary(felm( s_crime_inv~turnout_percentage + reservation+n_cand+dyn_won_earlier|factor(year)+factor(state_name), data =dyn_adr_ge_uniq_reg )) -->

<!-- ``` -->



<!-- #### assets  -->



<!-- ```{r} -->

<!-- summary(felm( log(total_assets)~turnout_percentage + reservation+n_cand+dyn_won_earlier|factor(year), data =dyn_adr_ge_uniq_reg )) -->

<!-- ``` -->

<!-- ### Census -->

<!-- ```{r} -->

<!-- cen <- read.csv("D:/cpr/data/census/pc_2011_census.csv") -->


<!-- cen$st_name <- tolower(cen$st_name) -->

<!-- dyn_adr_ge_uniq_cen <- inner_join(dyn_adr_ge_uniq, cen, by = c("state_name"= "st_name", "constituency_no"="pc_code")) -->

<!-- dyn_adr_ge_uniq_cen_reg <- inner_join(dyn_adr_ge_uniq_reg, cen, by = c("state_name"= "st_name", "constituency_no"="pc_code")) -->

<!-- ``` -->







<!-- ```{r} -->


<!-- ggplot(dyn_adr_ge_uniq_cen, aes(factor(dyn_con), WEALTHSCORE))+ -->
<!--   geom_boxplot() -->

<!-- ``` -->




<!-- ```{r} -->

<!-- summary(felm(WEALTHSCORE ~turnout_percentage + reservation+n_cand+dyn_con|factor(year)+factor(constituency_no)+factor(state_name), data =dyn_adr_ge_uniq_cen )) -->


<!-- ``` -->













