---
title: "Schools and Colleges"
author: "Najah"
date: "07/04/2021"
params:
  orig_date: "Original Publish Date: 7th March, 2021"
  update_date: !r paste("Updated on:", format(Sys.time(), '%d %B, %Y'))
authors:
  - najah
summary: Analysis of schools and colleges data
output:
  html_document:
    theme: flatly
    toc: TRUE
    toc_float: TRUE
    toc_depth: 5
    number_sections: TRUE
    fig_width: 6            
editor_options: 
  chunk_output_type: inline
---



### Document History

`r params$orig_date`

`r params$update_date`

---

```{r set up, warning=FALSE, include=FALSE, message= FALSE}
knitr::opts_chunk$set(cache = FALSE ,echo = FALSE, message=FALSE, warning = FALSE,fig.width = 16/2, fig.height = 9/2)
library(tidyverse)
library(data.table)
library(knitr)
library(kableExtra)
library(scales)
library(gridExtra)
library(stargazer)
library(ggbump)
library(cowplot)
library(colorspace)
library(ggthemes)
library(DT)
library(widgetframe)
`%!in%` = Negate(`%in%`)
select <- dplyr::select
```





# UP


The [All India Survey on Higher Education (AISHE)](http://aishe.nic.in/) website provided two kind of college data. 1, Colleges affiliated to Universities. 2, Stand alone institutions. 

There were *7690* affiliated colleges *1136* stand-alone colleges. Among these two categories, only *7718* observations had year of establishment. Once I filtered the list of colleges that provided the year of establishments to colleges that are established after 1974, the observations further came down to **7002**. This again reduced to **6825** after geocoding and chucking out the universities.




```{r}
college_up <- fread("D:/cpr/UP/dise/college_up_ac.csv")

college_up <- college_up %>% filter(year_estd>=1974 & Management != "University")  %>% select(-c(V1, Country, State))

#Hmisc::describe(college_up)
```

## Data summary{.tabset}

```{r}

 DT::datatable(head(college_up))

```

### Main variables

```{r}

names(college_up)

```

### types of management


```{r}
college_up %>% group_by(Management) %>% summarise(count = n())
```





### Year by year break-up of number of colleges

I kept *Private un-aided* as private and clubbed all others as government colleges.


```{r}

college_up$college_management <- ifelse(college_up$Management == "Private Un-Aided", "Private", "Government")

college_up %>% group_by(year_estd,college_management) %>% summarise(count = n()) %>% 
  ggplot(aes(factor(year_estd), count, fill =college_management))+
  geom_bar(position = "stack",stat = "identity")+
  labs(x = "Year")+
   theme_minimal()+
   theme(#axis.text.x = element_text(angle = 90),
        #legend.position = "bottom", 
     axis.text.y = element_text(size = 7))+
  coord_flip()
 

```


----

After my initial inspections, I went to merge the college data with UP dynasties data after allotting the coleges to each election year based on the year of establishment





```{r}
# names(college )
# 
# college_short <- college %>% select(c(election_type,year,constituency_no,85:101))

college_up <- college_up %>% mutate(year_el = case_when(
                                       year_estd >= 1974  & year_estd <= 1977 ~"1974",
                                       year_estd > 1977  & year_estd <= 1980 ~"1987",
                                       year_estd > 1980  & year_estd <= 1985 ~"1980",
                                       year_estd > 1985  & year_estd <= 1989 ~"1985",
                                       year_estd > 1989  & year_estd <= 1991 ~"1989",
                                       year_estd > 1991  & year_estd <= 1993 ~"1991",
                                       year_estd > 1993  & year_estd <= 1996 ~"1993",
                                       year_estd > 1996  & year_estd <= 2002 ~"1996",
                                       year_estd > 2002  & year_estd <= 2007 ~"2002",
                                       year_estd > 2007  & year_estd <= 2012 ~"2007",
                                       year_estd > 2012  & year_estd <= 2017 ~"2012",
                                       year_estd > 2017  & year_estd <= 2021 ~"2017"))

college_up %>% group_by(year_el) %>% summarise(count = n())


```


```{r}
# 
# names(college )
# 
# college_short <- college %>% select(c(election_type,year,constituency_no,85:101))

#college_up <-  college_up %>% mutate(management_1 = ifelse(Management =="Private Un-Aided", "Private","Government"))

college_up_n <- college_up %>% group_by(year_el, AC_NO) %>% dplyr::summarise(n_colleges = n(), n_private =length(college_name [college_management =="Private"]))

```




```{r dynasty merge}


dyn <- fread("D:/cpr/UP/up-dynasties/dyn_other_data/dyn_ae_ge.csv")

dyn_ae <- dyn %>% filter(election_type=="AE" & position ==1 &  year <=2017)

college_up_n$year_el <- as.numeric(college_up_n$year_el)

dyn_up_college <- right_join(college_up_n, dyn_ae, by = c("year_el" = "year", "AC_NO"="constituency_no"))



#dyn_college %>% replace_na(n_college, 0)

dyn_up_college$n_colleges <- replace_na(dyn_up_college$n_colleges, 0)

dyn_up_college$n_private <- replace_na(dyn_up_college$n_private, 0)

```



```{r}

## control

# dyn_college <- dyn_up_college %>% select(election_type, year_el, AC_NO, n_colleges) %>% arrange(year_el)%>% group_by( AC_NO)%>% mutate(college_cumsum = cumsum(n_colleges))  %>% rename(constituency_no = AC_NO, year = year_el)
# 
# write.csv(dyn_college, "D:/cpr/data/controls/up_college_ctrl.csv")

```

---

Average number of colleges built every year in a constituency is `r {round(mean(dyn_up_college$n_colleges),2)}`


<!-- ### Distribution of number of colleges established every election year in a constituency -->

<!-- ```{r} -->
<!-- ggplot(dyn_up_college, aes(n_colleges, color =year_el))+ -->
<!--   geom_density() -->

<!-- ``` -->


---




### Distribution of number of colleges in a constituency{.tabset}


This density chart shows the distribution of the number of colleges built in different constituencies during last 10 years

#### Post 2009

```{r}

dyn_up_college %>%filter(year_el >=2009) %>%  group_by( AC_NO) %>% summarise(count= sum(n_colleges)) %>% 

ggplot( aes(count))+
  geom_density()

```

---

#### Pre 2009

```{r}

dyn_up_college %>%filter(year_el <=2009) %>%  group_by( AC_NO) %>% summarise(count= sum(n_colleges)) %>% 

ggplot( aes(count))+
  geom_density()

```





## regressions{.tabset}




### Dynast definition 2{.tabset}

regression run on dynast definition 2

#### All years{.tabset}

In this regression we look at colleges built during the rule of MLAs selected during the election cycles starting from 1974 to 2017



```{r}
# fit.3 <- glm(linkage_down ~  caste_uc+ caste_yadav+caste_non_yadav_obc + caste_dalit + caste_muslim +minister_duration +industry + school_college + land + dynast+ post_90 +n_elections_w , family = binomial(link = "probit"))


dyn_up_college$caste_uc <- ifelse(dyn_up_college$caste_groups == "Upper Caste", 1,0)
dyn_up_college$caste_yadav <- ifelse(dyn_up_college$caste_groups == "Yadav", 1,0)
dyn_up_college$caste_muslim <- ifelse(dyn_up_college$caste_groups == "Muslim", 1,0)
dyn_up_college$caste_dalit <- ifelse(dyn_up_college$caste_groups == "Dalit", 1,0)
dyn_up_college$caste_non_yadav_obc <- ifelse(dyn_up_college$caste_groups == "Non-Yadav OBC", 1,0)



library(fixest)

fit.poisson <- feglm( n_colleges ~ dyn_cum_2+term_duration+turnout_percentage+ margin_percentage+constituency_type+enop+ log(electors) +caste_uc+ caste_yadav+caste_non_yadav_obc + caste_dalit + caste_muslim|year_el + constituency_name,data = dyn_up_college, family = "quasipoisson")





#summary(fit.poisson)

dyn_up_college$n_college_bin <- ifelse(dyn_up_college$n_colleges ==0,0,1)

fit.probit <- feglm( n_college_bin ~ dyn_cum_2+term_duration+turnout_percentage+ margin_percentage+enop+log(electors)+constituency_type+caste_uc+ caste_yadav+caste_non_yadav_obc + caste_dalit + caste_muslim |year_el +constituency_name ,family = binomial(link = "probit"),data = dyn_up_college)

# 
# summary(fit.probit)


```


```{r , results = "asis"}


etable(fit.poisson,fit.probit,cluster = "constituency_name",extraline=list("Caste control"=c("Yes", "Yes"))) %>% slice(-(10:14))%>% kable() %>% kable_styling(full_width = F)

```






#### Post 1991{.tabset}

- Tried post 1991 and 1996. Dynast co-effient on both are negative. The model below is post 1991.



```{r}
# fit.3 <- glm(linkage_down ~  caste_uc+ caste_yadav+caste_non_yadav_obc + caste_dalit + caste_muslim +minister_duration +industry + school_college + land + dynast+ post_90 +n_elections_w , family = binomial(link = "probit"))


dyn_up_college_91 <- dyn_up_college%>% filter(year_el>= 1991)


dyn_up_college_91$caste_uc <- ifelse(dyn_up_college_91$caste_groups == "Upper Caste", 1,0)
dyn_up_college_91$caste_yadav <- ifelse(dyn_up_college_91$caste_groups == "Yadav", 1,0)
dyn_up_college_91$caste_muslim <- ifelse(dyn_up_college_91$caste_groups == "Muslim", 1,0)
dyn_up_college_91$caste_dalit <- ifelse(dyn_up_college_91$caste_groups == "Dalit", 1,0)
dyn_up_college_91$caste_non_yadav_obc <- ifelse(dyn_up_college_91$caste_groups == "Non-Yadav OBC", 1,0)




fit.poisson <- feglm( n_colleges ~ dyn_cum_2+term_duration+turnout_percentage+ margin_percentage+enop+log(electors)+constituency_type +caste_uc+ caste_yadav+caste_non_yadav_obc + caste_dalit + caste_muslim |year_el +district_name ,family =  "quasipoisson",data = dyn_up_college_91)


#summary(fit.poisson)

dyn_up_college_91$n_college_bin <- ifelse(dyn_up_college_91$n_colleges ==0,0,1)

# fit.probit <- glm(data = dyn_up_college_91, n_college_bin ~ dyn_cum_2+caste_uc+ caste_yadav+caste_non_yadav_obc + caste_dalit + caste_muslim +factor(year_el ),family = binomial(link = "probit"))

fit.probit <- feglm( n_college_bin ~ dyn_cum_2+term_duration+turnout_percentage+ margin_percentage+enop+constituency_type +caste_uc+ caste_yadav+caste_non_yadav_obc + caste_dalit + caste_muslim+log(electors) |year_el +district_name ,family = binomial(link = "probit"),data = dyn_up_college_91)



#etable(fit.probit,cluster = "district_name") %>% kable()

```



```{r , results = "asis"}

etable(fit.poisson,fit.probit,cluster = "district_name",extraline=list("Caste control"=c("Yes", "Yes"))) %>% slice(-(10:14))%>% kable() %>% kable_styling(full_width = F)

```


#### 1993-2012 with night lights






```{r}


nl <- read.csv("D:/cpr/data/controls/nl_94_13.csv")


dyn_up_college_nl <- inner_join(dyn_up_college, nl, by = c("year_el" = "year", "AC_NO"= "constituency_no"))


schools <- read.csv("D:/cpr/data/controls/schools_ae_level_cumsum.csv")

school <- schools %>% select(year, constituency_no, n_schools = cumsum)


dyn_up_college_nl_sc <- inner_join(dyn_up_college_nl, schools, by = c("year_el"="year", "AC_NO"= "constituency_no"))
# 
#  fit.poisson <- glm(data = dyn_up_college_nl_sc, n_colleges ~ dyn_cum_2+ incumbent+margin_percentage+ turnout_percentage+enop+ term_duration+n_schools+ nl_tot+constituency_type+log(electors)+no_terms+enop*margin_percentage+log(electors)*factor(year_el)+factor(year_el) + district_name, family =  "quasipoisson")
# 
# 
# summary(fit.poisson)
```


```{r}
library(corrplot)

cor_dat <- dyn_up_college_nl_sc %>% select(n_colleges, dyn_cum_2, n_schools,incumbent,margin_percentage, turnout_percentage,enop, term_duration, nl_tot,year_el,electors)

corr <- cor(cor_dat)


corrplot(corr, method="circle")
```

----



```{r, results = "asis"}


library(fixest)

fit.poisson <-  feglm(n_colleges ~ dyn_cum_2+ incumbent+margin_percentage+ turnout_percentage+enop+ term_duration+n_schools+ nl_tot+constituency_type+log(electors)+no_terms|year_el + district_name, data = dyn_up_college_nl_sc,family= "quasipoisson")




dyn_up_college_nl_sc$n_college_bin <- ifelse(dyn_up_college_nl_sc$n_colleges ==0,0,1)

# fit.probit <- glm(data = dyn_up_college_91, n_college_bin ~ dyn_cum_2+caste_uc+ caste_yadav+caste_non_yadav_obc + caste_dalit + caste_muslim +factor(year_el ),family = binomial(link = "probit"))

fit.probit <- feglm(n_college_bin  ~ dyn_cum_2+ incumbent+margin_percentage+ turnout_percentage+enop+ term_duration+n_schools+ nl_tot+constituency_type+log(electors)+no_terms+caste_uc+ caste_yadav+caste_non_yadav_obc + caste_dalit + caste_muslim|year_el + district_name, data = dyn_up_college_nl_sc,family = binomial(link = "probit"))
  



etable(fit.poisson, fit.probit,cluster = "district_name") %>% kable(caption = "UP colleges - Poisson model") %>% kable_styling(full_width = F)

```





#### adr variables

Inorder to use the adr variables in the model, I have to limit the years to post 2009.

```{r}

 adr_up<- fread("D:/cpr/UP/up-dynasties/dyn_other_data/adr/up_12_adr_S.csv")




dyn_up_college_adr <- inner_join(dyn_up_college, adr_up, by =c("year_el" = "Year", "AC_NO"= "Constituency_No"))

dyn_up_college_adr$total_immovable_assets_totals <- ifelse(dyn_up_college_adr$total_immovable_assets_totals ==0,1,dyn_up_college_adr$total_immovable_assets_totals )

dyn_up_college_adr$total_movable_assets_totals <- ifelse(dyn_up_college_adr$total_movable_assets_totals ==0,1,dyn_up_college_adr$total_movable_assets_totals )

```



```{r, results = "asis"}

## caste



dyn_up_college_adr$caste_uc <- ifelse(dyn_up_college_adr$caste_groups == "Upper Caste", 1,0)
dyn_up_college_adr$caste_yadav <- ifelse(dyn_up_college_adr$caste_groups == "Yadav", 1,0)
dyn_up_college_adr$caste_muslim <- ifelse(dyn_up_college_adr$caste_groups == "Muslim", 1,0)
dyn_up_college_adr$caste_dalit <- ifelse(dyn_up_college_adr$caste_groups == "Dalit", 1,0)
dyn_up_college_adr$caste_non_yadav_obc <- ifelse(dyn_up_college_adr$caste_groups == "Non-Yadav OBC", 1,0)

dyn_up_college_adr$n_college_bin <- ifelse(dyn_up_college_adr$n_colleges ==0,0,1)


# 
# cor_dat <- dyn_up_college_adr %>% select(dyn_cum_2, incumbent,margin_percentage, turnout_percentage,enop, term_duration,electors,no_terms,total_immovable_assets_totals , total_movable_assets_totals, serious_crime,non_serious_crime,caste_uc, caste_yadav,caste_non_yadav_obc , caste_dalit , caste_muslim)
# 
# corr <- cor(cor_dat)
# 
# 
# corrplot(corr, method="circle")



fit.probit <- feglm(n_college_bin  ~ dyn_cum_2+ incumbent+margin_percentage+ turnout_percentage+enop+ term_duration+constituency_type+log(electors)+no_terms+log(total_immovable_assets_totals) + log(total_movable_assets_totals)+ non_serious_crime+caste_uc+ caste_yadav+caste_non_yadav_obc + caste_dalit + caste_muslim|year_el + district_name, data = dyn_up_college_adr,family = binomial(link = "probit"))
  
fit.probit_no_se <- feglm(n_college_bin  ~ dyn_cum_2+ incumbent+margin_percentage+ turnout_percentage+enop+ constituency_type+log(electors)+no_terms+log(total_immovable_assets_totals) + log(total_movable_assets_totals)+ serious_crime+non_serious_crime+caste_uc+ caste_yadav+caste_non_yadav_obc + caste_dalit + caste_muslim|year_el , data = dyn_up_college_adr,family = binomial(link = "probit"))


fit.poisson <- feglm(data = dyn_up_college_adr, n_colleges ~ dyn_cum_2+incumbent+margin_percentage+ turnout_percentage+enop+ constituency_type+log(electors)+caste_uc+ caste_yadav+caste_non_yadav_obc + caste_dalit + caste_muslim  + log(total_immovable_assets_totals) + log(total_movable_assets_totals)+ serious_crime+non_serious_crime|
                     year_el + district_name, family =  "quasipoisson")

#summary(fit.probit_no_se)

etable(fit.poisson, fit.probit, fit.probit_no_se,drop = c("caste_uc", "caste_yadav", "caste_non_yadav_obc" , "caste_dalit" , "caste_muslim") , subtitles = c("Poisson", "Probit", "Probit without SE Clustered"))



```


# India




There were **45022** affiliated colleges **11987** stand-alone colleges. Among these two categories, only **52232** observations had year of establishment. This further reduced  to  **49959**  observations after geocoding .






```{r}
college_in <- fread("D:/cpr/UP/dise/college_india_ac.csv")
```

## Data summary{.tabset}

### Year by year break-up of number of colleges


```{r}

college_in$college_management <- ifelse(college_in$Management == "Private Un-Aided", "Private", "Government")

college_in %>% filter(year_estd >1974) %>% group_by(year_estd,college_management) %>% summarise(count = n()) %>% 
  ggplot(aes(factor(year_estd), count, fill =college_management))+
  geom_bar(position = "stack",stat = "identity")+
  labs(x = "Year")+
   theme_minimal()+
   theme(#axis.text.x = element_text(angle = 90),
        #legend.position = "bottom", 
     axis.text.y = element_text(size = 6))+
  coord_flip()
 


```



---




### state break-up


```{r}
college_in %>% filter(year_estd >1974) %>% group_by(State,college_management) %>% summarise(count = n()) %>%
  ggplot(aes(reorder(State, -count), count, fill =college_management))+
  geom_bar(position = "stack",stat = "identity")+
  labs(x = "Year")+
   theme_minimal()+
   theme(#axis.text.x = element_text(angle = 90),
        #legend.position = "bottom", 
     axis.text.y = element_text(size = 6))+
  coord_flip()
```




----


We are focusing on data post 2009 since we only have pan-India dynasty data after 2009. Thus in our college data set before mergin with dynasty has **19148 ** observations.


```{r}
college_in <- college_in  %>% filter(year_estd >=2009 & Management != "University" )


college_in <- college_in %>% mutate(year_el = case_when(
                                       year_estd >=2009  & year_estd <= 2014 ~"2009",
                                       year_estd > 2014  & year_estd <= 2019 ~"2014",
                                       year_estd > 2019  & year_estd <= 2021 ~"2019"))


college_in$year_el <- as.numeric(college_in$year_el)

```





### State wise break-up post 2009



```{r}
college_in %>% filter(year_estd >1974) %>% group_by(State,college_management) %>% summarise(count = n()) %>%
  ggplot(aes(reorder(State, -count), count, fill =college_management))+
  geom_bar(position = "stack",stat = "identity")+
  labs(x = "Year")+
   theme_minimal()+
   theme(#axis.text.x = element_text(angle = 90),
        #legend.position = "bottom", 
     axis.text.y = element_text(size = 6))+
  coord_flip()
```



```{r}
college_in_n <- college_in %>% group_by(year_el, State,AC_NO) %>% dplyr::summarise(n_colleges = n(), n_private =length(college_name [college_management =="Private"]))

```




```{r dynasty }


dyn_ge <- fread("D:/cpr/UP/up-dynasties/dyn_other_data/tcpd_ge_09_14_19_dyn.csv")


college_in_n$State <- tolower(college_in_n$State)

dyn_ge$State_Name <- tolower(dyn_ge$State_Name)


dyn_in_college <- right_join(college_in_n, dyn_ge, by = c("State" = "State_Name","year_el" = "Year", "AC_NO"="Constituency_No"))



#dyn_college %>% replace_na(n_college, 0)

dyn_in_college$n_colleges <- replace_na(dyn_in_college$n_colleges, 0)

dyn_in_college$n_private <- replace_na(dyn_in_college$n_private, 0)



```


---

Average number of colleges built  in a constituency  in India during last 10 years is `r {round(mean(dyn_in_college$n_colleges),2)}`



### Distribution of number of colleges established every election year in a constituency

```{r}
ggplot(dyn_in_college, aes(n_colleges, color =year_el))+
  geom_density()

```

### Distributions of the number colleges established in the constituencies during 2009&2014

```{r}

dyn_in_college %>% group_by( AC_NO) %>% summarise(count= sum(n_colleges)) %>% 

ggplot( aes(count))+
  geom_density()

```

## regressions {.tabset}


All pan-india regressions are run on colleges built during 2009-19 at PC level.


### All colleges


```{r}

dyn_in_college <- dyn_in_college %>% ungroup()

fit.linear <- lm(data = dyn_in_college,n_colleges ~ dyn + State + factor(year_el)  )

#summary(fit.linear)

fit.logit <- glm(data = dyn_in_college, n_colleges ~ dyn + State + factor(year_el))


#summary(fit.logit)


fit.poisson <- glm(data = dyn_in_college, n_colleges ~ dyn + State + factor(year_el), family =  "quasipoisson")


#summary(fit.probit)

dyn_in_college$n_college_binary <- ifelse(dyn_in_college$n_colleges ==0,0,1)

fit.probit <- glm(data = dyn_in_college, n_college_binary ~ dyn + State + factor(year_el),family = binomial(link = "probit"))

```

```{r , results = "asis"}

stargazer(fit.linear, fit.logit, fit.poisson,fit.probit,title="Regression Results - India all colleges ",type = "html",
align=TRUE,  no.space=TRUE, keep = c("dyn" ),omit.stat=c("LL","ser","f"),
add.lines=list(c('Year fixed effects', 'Yes','Yes','Yes','Yes' ), c('State fixed effects', 'Yes','Yes','Yes','Yes')))

```






```{r , results = "asis"}

stargazer(fit.linear, fit.logit, fit.poisson,fit.probit,title="Regression Results - India private colleges ",type = "html",
align=TRUE,  no.space=TRUE, keep = c("dyn" ),omit.stat=c("LL","ser","f"),
add.lines=list(c('Year fixed effects', 'Yes','Yes','Yes','Yes' ), c('State fixed effects', 'Yes','Yes','Yes','Yes')))

```





---

### Model with controls - 2009 :2019




```{r}

## adr


# 
# shrug_adr_in <- shrug_adr_all %>% mutate(ac_no = as.numeric(str_sub(ac_id, -3)), .after = ac_id)
# 
# shrug_adr_in<- shrug_adr_in %>% filter(year %in% c(2009, 2014) & winner ==1)


adr <- fread("D:/cpr/UP/up-dynasties/dyn_other_data/adr/adr_tcpd_09_14_19.csv")

names(adr) <- tolower(names(adr))

adr_in <- adr %>% filter(position ==1) #%>% select(c(12:12,18:19,5:10,55:61))


adr_in$total_assets <- as.numeric(adr_in$total_assets)

adr_in$term_duration <- ifelse(adr_in$Year==2019,2,5)



adr_in <- adr_in %>% mutate(edu = case_when(education %in% c("5th Pass","10th Pass","8th Pass") ~"10",
                                  education == "12th Pass" ~"12",
                                  education %in% c("Graduate","Graduate Professional") ~"14",
                                  education == "Post Graduate" ~ "16",
                                  education == "Doctorate" ~"18",
                                  education %in% c("Literate","Others") ~"5",
                                  TRUE ~ "0"
                                  
                                  
                                  ))

adr_in$edu <- as.numeric(adr_in$edu )


dyn_in_college_adr <- inner_join(dyn_in_college, adr_in, by =c("State"="statename","year_el" = "year", "AC_NO"= "constituency_no"))




# dyn_in_college_adr <- inner_join(dyn_in_college, shrug_adr_in, by =c("State"="pc01_state_name","year_el" = "year", "AC_NO"= "ac_no"))

# tcpd_dyn <- fread("D:/cpr/data/tcpd/TCPD_GE_all.csv")
# 
# 
# inner_join(dyn_in)

```


```{r, results = "asis"}







fe2 <- fepois(n_colleges ~ dyn+ incumbent+margin_percentage+ turnout_percentage+enop+ +constituency_type+log(electors)+no_terms+log(total_assets)+serious_crime+non_serious_crime+edu+ position |year_el + State, data = dyn_in_college_adr,cluster = ~ State)

#summary(fe2)

etable(fe2) %>% kable(caption = "India colleges - Poisson model") %>% kable_styling(full_width = F)

# fit.poisson <- glm(data = dyn_in_college_adr, n_colleges ~ dyn+ log(total_assets)+ edu+serious_crime + non_serious_crime+term_duration+
#                      factor(year_el )+ State, family =  "quasipoisson")
# 
# names(dyn_in_college)
# 
# 
# 
# stargazer(fit.poisson,title="Regression Results - India  all colleges with adr ",type = "html",
# align=TRUE,  no.space=TRUE, keep = c("dyn" ,"total_assets", "edu","serious_crime", "non_serious_crime"),omit.stat=c("LL","ser","f"),
# add.lines=list(c('Year fixed effects', 'Yes','Yes','Yes','Yes' ), c('State fixed effects', 'Yes','Yes','Yes','Yes')))
```
