---
title: "MPLADS Carlos"
author: ""
params:
  orig_date: "Orignal Publish Date: 15 September 2021"
  update_date:  !r paste("Updated on:", format(Sys.time(), '%I:%m  %p -- %d %B, %Y'))
output: 
  html_document:
    theme: yeti
    toc: true
    toc_float: true
    number_sections: true
    fig_width: 6
editor_options:
  chunk_output_type: inline
---

------------------------------------------------------------------------

### Document history

`r params$orig_date`

`r params$update_date`

------------------------------------------------------------------------



```{r set up, echo =  FALSE, message = FALSE, warning = FALSE}

knitr::opts_chunk$set(cache = FALSE, echo =  FALSE, message = FALSE, warning = FALSE)
                      
         #fig.width = 16/2, fig.height = 9/2             

```

```{r libraries}

library(tidyverse)

library(data.table)

library(kableExtra)
library(scales)
library(haven)

library(lfe)

library(lme4)

# library(lmerTest)
library(stargazer)
`%!in%` = Negate(`%in%`)


select <- dplyr::select

```

<!-- # Fam df -->

```{r reading the main file}


fam_df <- read.csv("~/work/cpr/UP/up-dynasties/dyn_other_data/fam_df.csv")

fam_select <- fam_df %>% select(family_id, fam_type = success_cat)

dyn <- fread("~/work/cpr/UP/up-dynasties/dyn_other_data/dyn_ae_ge.csv") %>% 
  left_join(fam_select, by = "family_id") %>% 
  mutate(fam_type = replace_na(fam_type, "Non-Fam"))

# 
# 
# dyn %>% filter( position ==1 & fam_type == "Stable" &  year>2008) %>% select(year, constituency_name, candidate_name, party, dyn_cum_2) 
## filtering ge data to only 2009




```





# Audit data


Second part of carlos data that provides full information on MPLADS projects

## UP {.tabset}

In this section we look at the projets approved in 2009:14 session.



```{r}


mplads_car1 <- load("~/work/cpr/data/replication/carlos_mplads/data/mplads-eval-data.RData")

mplads.eval <- mplads.eval %>% mutate(work_cat = case_when(clean.sector %!in% c("roads", "education") ~ "other",
                                                           TRUE~as.character(clean.sector) ))

mplads.eval$work_cat <- factor(mplads.eval$work_cat , levels = c("roads", "education", "other"))

mplads_up <- mplads.eval %>% filter(state == "Uttar Pradesh" & session %in% c(14,15)) %>% mutate(year = ifelse(session==15, 2009, 2004))


##

mplads_car3 <- load("~/work/cpr/data/replication/carlos_mplads/data/mplads-data.RData")




```

```{r, results = "asis"}

dyn_ge_up <- dyn %>% filter(election_type == "GE" & position==1 & year %in% c( 2009))

dyn_ge_up$fam <- ifelse(dyn_ge_up$fam_type =="Stable" , "Stable"  , "Non-Family")




mplads_dyn_up <- inner_join(mplads_up,dyn_ge_up,by = c("year"= "year","idpc" = "constituency_no"))


mplads_dyn_up <- mplads_dyn_up%>% group_by(idpc) %>% 
  mutate(n_ac = n())
```


### top level summary

```{r, results = "asis"}
mplads_dyn_up%>% filter(year ==2009) %>% group_by(fam) %>% 
  summarise(count = n(),
            ngo = mean(ngo),
            completion_time = mean(comp_time, na.rm = TRUE),
            amount = mean(amt_sanc),
            n_proj_ac = mean(n_ac),
            mean_proj_el = mean(elec_yr),
            mean_app_time_wk = mean(app.time, na.rm = TRUE)
            ) %>% 
            kable(digits =0, type = "html") %>% 
            kable_styling()


```

### projects break-up

```{r}

mplads_dyn_up %>% group_by (year,fam, work_cat) %>% summarise(count = n()) %>% 
  group_by(year,fam) %>% mutate(sum = sum(count), prop= count /sum) %>% 
  ggplot(aes(fam, prop, fill= work_cat, label = ifelse(prop>.03, round(prop,2),"")))+
  geom_bar(stat = "identity",
           position = "stack")+
  geom_text(size = 3, position = position_stack(vjust = 0.5))+ 
    
    scale_x_discrete(labels = c("Non-Families","Families"))+
   scale_fill_grey()+
  facet_wrap(~year)+
    labs(title = " MPLADS projects composition",x = "", y = "Proportion", fill = "Type of work") +
 theme_minimal()+
  coord_fixed(ratio =2)+
  theme(plot.background = element_blank(),
        axis.line.x = element_line(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.y = element_blank(),
        #legend.position = "bottom",
        axis.title = element_blank(), 
        axis.text = element_text(size = 10),
        text = element_text(family = "serif")       )
```



### Approval time

**All**


```{r}


  ggplot(mplads_dyn_up %>% filter(app.time>0), aes(factor(year)
                                                   ,log(app.time+1)))+
  geom_boxplot()+
    geom_jitter(alpha = .3)+
   stat_summary(fun=mean, colour="darkred", geom="point",
               shape=15, size=1.5, show.legend=FALSE) +
  facet_wrap(~work_cat)+
  labs(title = "Average weeks to approval",
       y = "Log of weeks",
       x = "Project Type")+
  theme_light()+
  theme(axis.title.x =  element_blank())
#
#   ggplot(mp_car_dyn %>% filter(app.time>0), aes(reorder(clean.sector, -app.time, FUN = median),app.time))+
#   geom_boxplot()+
#     scale_y_log10()

```



**Family**

```{r}

  ggplot(mplads_dyn_up%>% filter(app.time>0 ), aes(fam,log(app.time+1)))+

  geom_boxplot()+
  geom_jitter(alpha = .3)+
   stat_summary(fun=mean, colour="darkred", geom="point", 
               shape=15, size=1.5, show.legend=FALSE) + 
  facet_wrap(~work_cat+year)+
labs(title = "Average weeks to approval",
       y = "Log of weeks",
       x = "Project Type")+
  theme_light()+
  theme(axis.title.x =  element_blank())
```


### Cost sanctioned

**Family**




```{r}


  ggplot(mplads_dyn_up%>% filter(app.time>0 ), aes(fam,log(amt_sanc+1)))+

  geom_boxplot()+
  geom_jitter(alpha = .3)+
   stat_summary(fun=mean, colour="darkred", geom="point", 
               shape=15, size=1.5, show.legend=FALSE) + 
  facet_wrap(~work_cat+year)+
  labs(title = "Average amount sanctioned",
       y = "Log of amount sanctioned",
       x = "Project Type")+
  theme_light()+
  theme(axis.title.x =  element_blank())

```

## India {.tabset}

In this section we look at the projects approved during 14th & 15the session for 12 Indian states. They are chhattisgarh, gujarat,       haryana,himachal pradesh, jammu and kashmir, karnataka, madhya pradesh,maharashtra, punjab, rajasthan, uttar pradesh and uttarakhand.


```{r}
mplads_all <- mplads.eval %>%rename_all(tolower) %>% mutate(state = tolower(state)) %>% 
  filter(!is.na(idpc) & session %in% c(15,14)) %>% mutate(year = ifelse(session==15, 2009, 2004))


   
  dyn_ge  <- read_csv("~/work/cpr/UP/up-dynasties/dyn_other_data/dyn_5pc_8919.csv") %>% 
    filter(position ==1 & year %in% c(2009,2004))%>% 
    distinct(year,state_name, constituency_no, position, .keep_all = TRUE) %>% 
    select(state_name, constituency_no,constituency_name, dynast = dyn, year) %>% 
    mutate(state_name = tolower(state_name),
           state_name = ifelse(state_name =="jammu & kashmir",
                               "jammu and kashmir", state_name),
           fam= ifelse(dynast ==1,"Family","Non-Family"),
           fam = ifelse(is.na(fam),"Non-Family", fam)) %>% 
    filter(state_name %in% c("chhattisgarh" , "gujarat",          
  "haryana","himachal pradesh", 
 "jammu and kashmir", "karnataka",        
 "madhya pradesh","maharashtra",      
 "punjab"  ,"rajasthan",        
"uttar pradesh" ,"uttarakhand" ))
  
  
  mplads_dyn <- inner_join(mplads_all,dyn_ge, by = c("year" = "year",
                                                     "state"= "state_name",
                                                     "idpc"= "constituency_no") )


    
  mplads_dyn  <-  mplads_dyn  %>% group_by(state,idpc) %>% 
  mutate(n_ac = n())
```



### top level summary

```{r, results = "asis"}


mplads_dyn%>%  group_by(fam) %>%  
  summarise(count = n(),
            ngo = mean(ngo, na.rm = TRUE),
            #completion_time = mean(comp_time, na.rm = TRUE),
            amount = mean(amt_sanc),
            n_proj_ac = mean(n_ac),
            mean_app_time = mean(app.time, na.rm = TRUE)
            ) %>% 
            kable(digits =0, type = "html") %>% 
            kable_styling()


```

### projects break-up

```{r}

mplads_dyn%>% group_by (fam,year, work_cat) %>% summarise(count = n()) %>% 
  group_by(fam, year) %>% mutate(sum = sum(count), prop= count /sum) %>% 
  ggplot(aes(fam, prop, fill= work_cat, label = ifelse(prop>.03, round(prop,2),"")))+
  geom_bar(stat = "identity",
           position = "stack")+
    facet_wrap(~year)+
  geom_text(size = 3, position = position_stack(vjust = 0.5))+ 

    scale_x_discrete(labels = c("Non-Families","Families"))+
   #scale_fill_grey()+
    labs(title = " MPLADS projects composition",x = "", y = "Proportion", fill = "Type of work") +
 theme_minimal()+
  coord_fixed(ratio =2)+
  theme(plot.background = element_blank(),
        axis.line.x = element_line(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.y = element_blank(),
        #legend.position = "bottom",
        axis.title = element_blank(), 
        axis.text = element_text(size = 10),
        text = element_text(family = "serif") )
```


### Approval time

**All**




```{r}


  ggplot(mplads_dyn%>% filter(app.time>0), aes(factor(year),log(app.time+1)))+
  geom_boxplot()+
    geom_jitter(alpha = .1)+
  facet_wrap(~work_cat, nrow =2)+
   stat_summary(fun=mean, colour="darkred", geom="point", 
               shape=15, size=1.5, show.legend=FALSE) + 
  labs(title = "Average weeks to approval",
       y = "Log of weeks",
       x = "Project Type")+
  theme_light()+
  theme(axis.title.x =  element_blank())
# 
#   ggplot(mp_car_dyn %>% filter(app.time>0), aes(reorder(clean.sector, -app.time, FUN = median),app.time))+
#   geom_boxplot()+
#     scale_y_log10()
   
```

---

**Family**

```{r}

  ggplot(mplads_dyn%>% filter(app.time>0 ), aes(fam,log(app.time+1)))+

  geom_boxplot()+
  geom_jitter(alpha = .1)+
   stat_summary(fun=mean, colour="darkred", geom="point", 
               shape=15, size=1.5, show.legend=FALSE) + 
  facet_wrap(~work_cat,scales = "fixed", nrow =2)+
labs(title = "Average weeks to approval",
       y = "Log of weeks",
       x = "Project Type")+
  theme_light()+
  theme(axis.title.x =  element_blank())
```



### Cost sanctioned

**All*

```{r}

  ggplot(mplads_dyn%>% filter(app.time>0), aes(factor(year),log(amt_sanc+1)))+
  geom_boxplot()+
    geom_jitter(alpha = .1)+
   stat_summary(fun=mean, colour="darkred", geom="point", 
               shape=15, size=1.5, show.legend=FALSE) +
  facet_wrap(~work_cat, nrow =2)+
  labs(title = "Average amount sanctioned",
       y = "Log of amount sanctioned",
       x = "Project Type")+
  theme_light()+
  theme(axis.title.x =  element_blank())
```

---

**Family**

```{r}


  ggplot(mplads_dyn %>% filter(app.time>0 ), aes(fam,log(amt_sanc+1)))+

  geom_boxplot()+
  geom_jitter(alpha = .1)+
   stat_summary(fun=mean, colour="darkred", geom="point", 
               shape=15, size=1.5, show.legend=FALSE) + 
  facet_wrap(~work_cat,scales = "fixed", nrow =2)+
  labs(title = "Average amount sanctioned",
       y = "Log of amount sanctioned",
       x = "Project Type")+
  theme_light()+
  theme(axis.title.x =  element_blank())

```

# Bureaucrats data 
First part of carlos data that provides limited information on MPLADS projects, but a huge dataset with ~3 lakhs obs. for pan-india and for different sessions


## India {.tabset}


```{r}
remove <- c("\\(sc\\)", "\\(st\\)")

mplads_br <- mplads %>%rename_all(tolower) %>% mutate(state = tolower(state)) %>% 
  filter( session %in% c(15,14)) %>% mutate(year = ifelse(session==15, 2009, 2004)) %>% 
  mutate(pc_name = str_trim(str_remove(tolower(constituency.name),paste(remove, collapse=  "|")
         )))
```


```{r}
dyn_ge1  <- read_csv("~/work/cpr/UP/up-dynasties/dyn_other_data/dyn_5pc_8919.csv") %>% 
    filter(position ==1 & year %in% c(2009,2004))%>% 
    distinct(year,state_name, constituency_no, position, .keep_all = TRUE) %>% 
    select(state_name, constituency_no,constituency_name, dynast = dyn, year) %>% 
    mutate(state_name = tolower(state_name),
           constituency_name = tolower(constituency_name),
           state_name = ifelse(state_name =="jammu & kashmir",
                               "jammu and kashmir", state_name),
           fam= ifelse(dynast ==1,"Family","Non-Family"),
           fam = ifelse(is.na(fam),"Non-Family", fam)) %>% 
  filter(state_name  %!in% c("andhra pradesh", "telengana"))
 
 


mplads_br <- mplads_br %>% mutate(state = tolower(state),
                                  pc_name = tolower(pc_name),
                     state_name = case_when(state == "himachal pr." ~"himachal pradesh" ,
                                            state == "j & k"  ~"jammu and kashmir",
                                            TRUE ~state))

```


```{r}

mplads_br_dyn <- inner_join(dyn_ge1, mplads_br, by = c(year = "year",state_name = "state_name",constituency_name = "pc_name"))

```


```{r}

  
  

mplads_br_dyn <- mplads_br_dyn%>%  mutate(completed = ifelse(work.status== "COMPLETED", 1,0),
                                               
                                               party_bjp = ifelse(pty_n =="BJP", 1,0),
                                               party_inc = ifelse(pty_n =="INC",1,0),
                                               party_bsp = ifelse(pty_n =="BSP",1,0),
                                               party_sp
                                               = ifelse(pty_n =="SP",1,0),
                                               )



```

### Top level summary

```{r}
mplads_br_dyn%>% group_by(fam) %>% 
  summarise(n_projects = n(),
            n_pc = n_distinct(constituency_name),
            avg_proj_pc = n_projects/n_pc,
            avg_days_approv = mean(app.time*7, na.rm = TRUE),
            avg_cost = mean(cost.sanc, na.rm = TRUE),
            avg_unfinished = mean(unfinish*100),
            completed = mean(completed)
            ) %>% 
  kable(digits = 2) %>% 
  kable_styling()
```

### weeks for approval

```{r, weeks in}
ggplot(mplads_br_dyn, aes(fam, log(app.time+1)))+
  geom_boxplot()+
  facet_wrap(~year)+
  labs(title = "Weeks to approve proposal",
       subtitle = "Loksabha MPs - 2009:14",
       y = "log of weeks",
       x="Legislator")+
  theme_light()
```

### Cost per project

```{r cost in }
ggplot(mplads_br_dyn, aes(fam, log(cost.sanc+1)))+
  geom_boxplot()+
  facet_wrap(~year)+
  labs(title = "Project costs",
       subtitle = "UP Loksabha MPs - 2009:14",
       y = "log of cost",
       x="Legislator")+
  theme_light()
```

### Number of projects in PCs

```{r n proj in }


n_proj_df<- mplads_br_dyn %>% group_by(year, constituency_name, fam) %>% summarise(count = n())  
n_proj_bp <- ggplot(n_proj_df, aes(fam, log(count)))+
  geom_boxplot()+
  facet_wrap(~year)+
  labs(title = "Number of projects in PCs",
       subtitle = " Loksabha MPs - 2004:14",
       y = "log of count",
       x="Legislator")+
  theme_light()

n_proj_dens <-ggplot(n_proj_df, aes( log(count+1), fill = fam))+
    geom_density(alpha = .5)+
  facet_wrap(~year)+
    labs(title = "Number of projects in PCs",
         subtitle = "Loksabha MPs - 2004:14",
         y = "log+1 of count",
         x="Legislator")+
    theme_light()+
    theme(legend.position = "bottom")

library(patchwork)

n_proj_bp +  n_proj_dens


```

## UP {.tabset}



```{r}


mplads_09_up <- mplads_br %>% filter(session %in% c(14,15) & state == "uttar pradesh") 

dyn_ge_up <- dyn_ge1 %>% mutate( constituency_name= str_trim(tolower(constituency_name)),
                                       constituency_name = ifelse(constituency_name=="gautam buddh nagar","gautam buddha nagar", constituency_name)) %>% 
  filter(year %in% c(2004, 2009) & state_name == "uttar pradesh")

# up_pc_uniq <- mplads_09_up %>% distinct(pc_name)
# dyn_pc_uniq <- dyn_ge_w_09 %>% distinct(constituency_name)
# 
# inner_join(dyn_pc_uniq, up_pc_uniq, by = c(constituency_name = "pc_name"))

mplads_dyn_up09 <- inner_join(mplads_09_up , dyn_ge_up, by = c( "year"= "year","pc_name" = "constituency_name"))

mplads_dyn_up09 <- mplads_dyn_up09 %>%  mutate(completed = ifelse(work.status == "COMPLETED", 1,0),
                                              
                                               party_bjp = ifelse(pty_n =="BJP", 1,0),
                                               party_inc = ifelse(pty_n =="INC",1,0),
                                               party_bsp = ifelse(pty_n =="BSP",1,0),
                                               party_sp
                                               = ifelse(pty_n =="SP",1,0),
                                               )



```

### Top level summary

```{r}
mplads_dyn_up09 %>% group_by(fam) %>% 
  summarise(n_projects = n(),
            n_pc = n_distinct(pc_name),
            avg_proj_pc = n_projects/n_pc,
            avg_days_approv = mean(app.time*7, na.rm = TRUE),
            avg_cost = mean(cost.sanc, na.rm = TRUE),
            avg_unfinished = mean(unfinish*100),
            completed = mean(completed)
            ) %>% 
  kable(digits = 2) %>% 
  kable_styling()
```

### weeks for approval

```{r, weeks}
ggplot(mplads_dyn_up09, aes(fam, log(app.time+1)))+
  geom_boxplot()+
  facet_wrap(~year)+
  labs(title = "Weeks to approve proposal",
       subtitle = "UP Loksabha MPs - 2009:14",
       y = "log of weeks",
       x="Legislator")+
  theme_light()
```

### Cost per project

```{r cost }
ggplot(mplads_dyn_up09, aes(fam, log(cost.sanc+1)))+
  geom_boxplot()+
  facet_wrap(~year)+
  labs(title = "Project costs",
       subtitle = "UP Loksabha MPs - 2009:14",
       y = "log of cost",
       x="Legislator")+
  theme_light()
```

### Number of projects in PCs

```{r n proj }


n_proj_df<- mplads_dyn_up09 %>% group_by(year, fam,pc_name) %>% summarise(count = n())  
n_proj_bp <- ggplot(n_proj_df, aes(fam, log(count)))+
  geom_boxplot()+
  facet_wrap(~year)+
  labs(title = "Number of projects in PCs",
       subtitle = "UP Loksabha MPs - 2009:14",
       y = "log+1 of count",
       x="Legislator")+
  theme_light()

n_proj_dens <-ggplot(n_proj_df, aes( log(count+1), fill = fam))+
    geom_density(alpha = .5)+
  facet_wrap(~year)+
    labs(title = "Number of projects in PCs",
         subtitle = "UP Loksabha MPs - 2009:14",
         y = "log+1 of count",
         x="Legislator")+
    theme_light()+
  theme(legend.position = "bottom")

library(patchwork)

n_proj_bp +  n_proj_dens


```

<!-- ### Models {.tabset} -->

<!-- ```{r} -->


<!-- df <- mplads_dyn_up09 %>%  -->
<!--    group_by(pc_name) %>% mutate(n_proj_pc = n()) %>% ungroup() %>%  -->

<!--   select(n_proj_pc, approval_time = app.time , cost_sanctioned = cost.sanc , fam ,cpwork ,  poweryr ,  national , govcol, reserved , margin.x , turnout , ncan,party_bjp , party_inc ,party_sp , party_bsp, tot.dis.works , mp.per.dis,  gdppc , rugged, pc_name) %>% mutate(approval_time = log(approval_time+1),  cost_sanctioned = log(cost_sanctioned+1))  %>%mutate(                                                                                                                                                                                                                                                  gdppc = log(gdppc+1), -->
<!--                                                                                                                                                                                                                                                                                                                      rugged = log(rugged+1)) %>%  -->
<!--   filter(cost_sanctioned>0 & approval_time>0) -->




<!-- ``` -->


<!-- #### Data summary -->


<!-- ```{r} -->


<!-- mean1 <- df %>% summarise_at(c(1:20),~ mean(.x, na.rm = TRUE)) %>% transpose() %>% setNames("Mean") -->

<!-- min1 <- df %>% summarise_at(c(1:20),~ min(.x, na.rm = TRUE))%>% transpose()%>% setNames("Min") -->

<!-- max1 <- df %>% summarise_at(c(1:20),~ max(.x, na.rm = TRUE))%>% transpose()%>% setNames("Max") -->


<!-- sd1 <- df %>% summarise_at(c(1:20),~ sd(.x, na.rm = TRUE))%>% transpose()%>% setNames("SD") -->



<!-- na1 <- df %>% -->
<!--   summarise_all(funs(sum(is.na(.))))%>% transpose()%>% slice(1:20)%>% setNames("NA") -->

<!-- vars1 <- c("Number of projects (PC)","Log(Approval Time)","Log(Cost Sanctioned)",  -->
<!--            "State Alignment","Stable Family",  "CM Tenure", "National Party", -->
<!--            "Centre Alignment", "Reserved PC","Margin", "Turnout", "Number of Candidates", -->
<!--            "Party: BJP",   "Party: INC", -->
<!--            "Party: SP","Party BSP", "Number of Works: District", "MPs per District", -->
<!--            "Log(Rugged)", "Log(GDP per Capita)") %>% as.data.frame() %>% slice(1:20) %>% setNames("variable") -->

<!-- cbind(vars1, mean1, min1, max1, sd1, na1) %>%  -->
<!--   kable(digits = 2,) %>%  -->
<!--   kable_styling(full_width = F) -->

<!-- ``` -->


<!-- #### Models sub{.tabset} -->

<!-- ##### Approval time -->


<!-- ```{r,results="asis"} -->


<!-- fit_time1 <- felm(approval_time ~ cost_sanctioned+cpwork +  stable_binary,data = df) -->

<!-- fit_time2 <- lmer(approval_time ~ cost_sanctioned+ cpwork + stable_binary+(1|pc_name),data = df) -->

<!-- fit_time3 <- lmer(approval_time ~ cost_sanctioned+ cpwork + stable_binary+ national+ poweryr +(1|pc_name),data = df) -->

<!-- fit_time4 <- lmer(approval_time ~ cost_sanctioned+ cpwork + stable_binary+ national+ poweryr + ncan+rugged+ (1|pc_name),data = df) -->

<!-- fit_time <- lmer(approval_time ~ cost_sanctioned+ stable_binary +cpwork +  poweryr +  national + govcol+ reserved + margin.x + turnout + ncan+party_bjp + party_inc +party_sp + party_bsp+ tot.dis.works + mp.per.dis+  gdppc + rugged + (1|pc_name),data = df) -->

<!-- lines <-  list (c("RE Parliamentary Constituency", "No","Yes", "Yes", "Yes", "Yes")) -->

<!-- labs <- c( "Log Cost Sanctioned",  -->
<!--            "State Alignment","Stable Family",  "CM Tenure", "National Party", -->
<!--            "Centre Alignment", "Reserved PC","Margin", "Turnout", "Number of Candidates", -->
<!--            "Party: BJP",   "Party: INC", -->
<!--            "Party: SP", "Number of Works: District", "MPs per District", -->
<!--            "Log(Rugged)", "Log(GDP per Capita)", "Intercept" -->
<!--           ) -->

<!-- stargazer(fit_time1, -->
<!--           fit_time2, -->
<!--           fit_time3, -->
<!--           fit_time4, -->
<!--           fit_time, -->
<!--           type = "html", -->
<!--           add.lines = lines, -->
<!--           covariate.labels = labs, -->
<!--           dep.var.caption = "Log(Approval time- weeks)", -->
<!--           dep.var.labels.include = FALSE -->
<!--           ) -->

<!-- ``` -->

<!-- ##### Cost Sanctioned -->

<!-- ```{r, results="asis"} -->

<!-- fit_cost1 <- felm(cost_sanctioned~approval_time+cpwork +  stable_binary,data = df) -->

<!-- fit_cost2 <- lmer(cost_sanctioned~approval_time+ cpwork + stable_binary+(1|pc_name),data = df) -->

<!-- fit_cost3 <- lmer(cost_sanctioned~approval_time+ cpwork + stable_binary+ national+ poweryr +(1|pc_name),data = df) -->

<!-- fit_cost4 <- lmer(cost_sanctioned~approval_time+ cpwork + stable_binary+ national+ poweryr + ncan+rugged+ (1|pc_name),data = df) -->

<!-- fit_cost <- lmer(cost_sanctioned~approval_time+ stable_binary +cpwork +  poweryr +  national + govcol+ reserved + margin.x + turnout + ncan+party_bjp + party_inc +party_sp + party_bsp+ tot.dis.works + mp.per.dis+  gdppc + rugged + (1|pc_name),data = df) -->

<!-- lines <-  list (c("RE Parliamentary Constituency", "No","Yes", "Yes", "Yes", "Yes")) -->

<!-- labs <- c( "Log Approval Time",  -->
<!--            "State Alignment","Stable Family",  "CM Tenure", "National Party", -->
<!--            "Centre Alignment", "Reserved PC","Margin", "Turnout", "Number of Candidates", -->
<!--            "Party: BJP",   "Party: INC", -->
<!--            "Party: SP", "Number of Works: District", "MPs per District", -->
<!--            "Log(Rugged)", "Log(GDP per Capita)", "Intercept" -->
<!--           ) -->

<!-- stargazer(fit_cost1, -->
<!--           fit_cost2, -->
<!--           fit_cost3, -->
<!--           fit_cost4, -->
<!--           fit_cost,type = "html", -->
<!--           add.lines = lines, -->
<!--           covariate.labels = labs, -->
<!--           dep.var.caption = "Log(Cost sanctioned)", -->
<!--           dep.var.labels.include = FALSE -->

<!--           ) -->

<!-- ``` -->

