---
title: "PMGSY Analysis"
author: ""
date: "2020-06-19"
params:
  orig_date: "Original Publish Date: 19 June, 2020"
  update_date: !r paste("Updated on:", format(Sys.time(), '%d %B, %Y'))
output:
  html_document:
    theme: readable
    toc: TRUE
    toc_float: TRUE
    toc_depth: 5
    number_sections: false
    fig_width: 6            
editor_options: 
  chunk_output_type: inline

---

---

### Document History

`r params$orig_date`

`r params$update_date`

---
```{r set up, warning=FALSE, include=FALSE, message= FALSE}

knitr::opts_chunk$set(cache = FALSE,echo = FALSE, message=FALSE, warning = FALSE)

##fig.width = 16/2, fig.height = 9/2

library(tidyverse)
library(data.table)
library(knitr)
library(kableExtra)
library(scales)
library(gridExtra)
`%!in%` = Negate(`%in%`)
```

# PMGSY

## summary stats {.tabset}



```{r file config}


dyn <- fread("~/work/cpr/UP/up-dynasties/dyn_other_data/dyn_ae_ge.csv", header = TRUE)


dyn$dyn_cum_2_text <- ifelse(dyn$dyn_cum_2 ==0, "Non-family","Family")
pmgsy<- fread("~/work/cpr/UP/up-dynasties/dyn_other_data/pmgsy.csv", stringsAsFactors = FALSE)

pmgsy <- pmgsy %>% mutate(year_ac = as.numeric(case_when(`Sanctioned Year` %in% c("2007 - 2008", "2009 - 2010","2010 - 2011","2011 - 2012")~"2007",
                                     `Sanctioned Year` =="2012 - 2013" ~"2012",
                                     `Sanctioned Year` =="2018 - 2019" ~"2017",
                                     TRUE~ "Others"
                                     )))

#glimpse(pmgsy)


names(pmgsy) <- tolower(names(pmgsy))

pmgsy <- pmgsy %>% select(year, everything())%>%  select(- c(2:78)) %>% rename(constituency_no = `pc no`) %>% filter(year != 2014)

dyn_ge_w <- dyn %>% filter(election_type == "GE" & position==1)

dyn_ae_w <- dyn %>% filter(election_type == "AE" & position==1)

dyn_ae_pmgsy <- inner_join(pmgsy, dyn_ae_w, by = c("year_ac" = "year", "ac no" = "constituency_no"))


dyn_pmgsy <- merge(pmgsy,dyn_ge_w, by = c("year", "constituency_no"))

#dyn_pmgsy$dyn_cum_2_text <- ifelse(dyn_pmgsy$dyn_cum_2 ==0, "Non-family","Family")

#summary(pwd)


names(dyn_pmgsy) <- make.unique(names(dyn_pmgsy))

dyn_pmgsy$fam_rel_id_uniq <-  paste(dyn_pmgsy$family_id, dyn_pmgsy$rel_id_uniq,sep = "")

dyn_pmgsy  <- dyn_pmgsy %>% group_by(fam_rel_id_uniq) %>% mutate(n_proj_ind = n())



```

### Summary stats






```{r}


dyn_pmgsy %>% group_by(year) %>% summarise(count = n(), sum(`road length (kms)`), sum(sanctionedcostnew)) %>% kable(caption = "PMGSY across years" ,col.names = c ("Loksabha Term", "Number of projects", "Length coverd (Kms)", "Total sanctioned amount (Lakhs)"),digits = 0)%>% kable_styling(bootstrap_options = "striped")


```

## Constituency type

```{r}


dyn_pmgsy$sanc_cost_rup <-(dyn_pmgsy$sanctionedcostnew)*100000

dyn_pmgsy <- dyn_pmgsy %>% group_by(year,constituency_no) %>% mutate(ac_proj_no = n())


 

#  dyn_pmgsy  %>% group_by(dyn_cum_2_text) %>% summarise(mean_proj = mean(ac_proj_no), mean_cost = mean(sanc_cost_rup ), mean_rd_len = mean(`road length (kms)`))
# 
# #,sum_rd = sum(`road length (kms)`),sum_cost = sum(`sanction cost`), cost_p_km = (sum_rd/sum_cost)*100000) 
# 
# 
# Entity <- c("Non-family", "Family")
#  
#  cbind(Entity,dyn_pmgsy_mean) %>% select(-dyn_cum_2) %>%  kable(caption = "PMGSY summary wrt constituency type", col.names = c ("Type of constituency", "Average number of projects","Avergae expenditure per project", "Average road length (km)"),digits = 1)%>% kable_styling(bootstrap_options = "striped")

 #summary(pmgsy)
 
 
 dyn_pmgsy %>% group_by(dyn_cum_2_text) %>% summarise(sum = sum(`road length (kms)`), count = n_distinct(constituency_no),mean_proj_con = n()/count,mean_proj = mean(`road length (kms)`), mean_con = sum/count) %>% select(dyn_cum_2_text,mean_proj_con,mean_proj, mean_con) %>% kable(caption = "PMGSY summary stats wrt constituency type", col.names = c("Constituency Type","Average number of projects"," Average length per project", "Average length over all"),digits = 1)%>% kable_styling(bootstrap_options = "striped")





```






## Experience categories 


```{r}

dyn_pmgsy  <- dyn_pmgsy %>% group_by(fam_rel_id_uniq) %>% mutate(n_proj_ind = n())


dyn_pmgsy  %>% group_by(fam_exp_cum_cat) %>% summarise(mean_proj = mean(n_proj_ind), mean_cost = sum(sanctionedcostnew)/n_distinct(fam_rel_id_uniq), mean_rd_len =sum(`road length (kms)`)/n_distinct(fam_rel_id_uniq)) %>% kable(caption = "PMGSY road stats wrt to experience categories", col.names = c("Expereince Category", "Average number of projects", "Average cost (Lakhs)", "Average road length"), digits = 0) %>% kable_styling(bootstrap_options = "striped")
```

 
## Caste


```{r}

#summarise(proj =n()/n_distinct(constituency_no), len = sum(`road length`)/n_distinct(constituency_no)) 

dyn_pmgsy  <- dyn_pmgsy %>% group_by(fam_rel_id_uniq) %>% mutate(n_proj_ind = n())


dyn_pmgsy  %>% group_by(caste_groups) %>% summarise(mean_proj = mean(n_proj_ind), mean_cost = sum(sanctionedcostnew)/n_distinct(fam_rel_id_uniq), mean_rd_len =sum(`road length (kms)`)/n_distinct(fam_rel_id_uniq)) %>% arrange(-mean_proj) %>% kable(caption = "PMGSY road stats wrt to caste groups", col.names = c("Caste group", "Average number of projects", "Average cost", "Average road length"), digits = 0) %>% kable_styling(bootstrap_options = "striped")





```





## Contractors




### Constituency type

#### PC

```{r}


dyn_pmgsy <- dyn_pmgsy %>% group_by(constituency_no) %>% mutate(cont_uniq = n_distinct(`contractor name`))


dyn_pmgsy  <- dyn_pmgsy %>% group_by(fam_rel_id_uniq) %>% mutate(n_cont_ind = n_distinct(`contractor name`))

dyn_pmgsy %>% group_by(dyn_cum_2_text) %>% summarise(mean(n_cont_ind),sum(sanctionedcostnew)/n_distinct(`contractor name`)) %>% 
kable(caption = "PMGSY average number of contractors and amount sanctioned  wrt constituency type", col.names = c ("Type of constituency", "Average number of unique contractors", "AAvergae amount sanctioned to a unique contractor (Lakhs)"),digits = 0)%>% kable_styling(bootstrap_options = "striped")

```

#### AC


```{r}


dyn_ae_pmgsy %>% filter(year_ac!= 2012)%>%  group_by(dyn_cum_2_text) %>% summarise(n_projects = n(),uniq_contractors = n_distinct(`contractor name`), mean_uniq_contractors = n_projects/uniq_contractors, tot_cost = sum(sanctionedcostnew), mean_cost_project = tot_cost/n_projects, mean_cost_uniq_cotractor = mean_cost_project*mean_uniq_contractors) %>% select(-c("tot_cost"))%>% 
  kable(digits = 1,caption = "pmgsy at ac level", col.names =c("Entity","total projects", "Unique contractors","Avg. uniq contractors","Avg. cost per project","Avg. amount recieved by unique contractor")) %>% 
  kable_styling()

```



### Experience categories

```{r}
dyn_pmgsy %>% group_by(fam_exp_cum_cat) %>% summarise(mean(n_cont_ind),sum(sanctionedcostnew)/n_distinct(`contractor name`)) %>% 
kable(caption = "PMGSY average number of contractors and amount sanctioned  wrt experience category", col.names = c ("Experience category", "Average number of unique contractors", "Avergae amount sanctioned to a unique contractor (Lakhs)"),digits = 0)%>% kable_styling(bootstrap_options = "striped")
```



### Caste

```{r}



dyn_pmgsy %>% group_by(caste_groups) %>% summarise(mean(n_cont_ind),sum(sanctionedcostnew)/n_distinct(`contractor name`)) %>% 
kable(caption = "PMGSY average number of contractors and amount sanctioned  wrt caste group of the politician", col.names = c ("TCaste group", "Average number of unique contractors", "Avergae amount sanctioned to unique contractors (Lakhs)"),digits = 0)%>% kable_styling(bootstrap_options = "striped")



```


# AC level data


```{r}

pmgsy_ac <- fread("~/work/cpr/data/up_misc/merged_ac_all.csv")

#names(pmgsy_ac)

pmgsy_ac <-pmgsy_ac %>% group_by(year,constituency_no) %>% summarise(length = sum(`Road Length (Kms)`, na.rm = TRUE), n_roads = n(), cost = sum(`Sanction Cost`, na.rm = TRUE))


dyn <- fread("~/work/cpr/UP/up-dynasties/dyn_other_data/dyn_all.csv")

dyn <- dyn %>% filter(year %in% c(2007, 2012)&position ==1&election_type=="AE")

dyn_pmgsy <- left_join( dyn,pmgsy_ac, by = c("year", "constituency_no"))



nl <- fread("~/work/cpr/data/controls/nl_94_13.csv", header = TRUE)

nl <- nl %>% filter(year %in% c(2007, 2012))


dyn_pmgsy <- right_join( nl,dyn_pmgsy, by = c( "year", "constituency_no"))



```
### Summary of the data {.tabset}


Data is available for two years 2007 and 2012. So we expect to have 403*2 = 806 observations.



#### Missing values




```{r}

dyn_pmgsy %>% summarise_at(c("length", "n_roads","cost"), ~sum(is.na(.)))

```


```{r}
#"/" <- function(x,y) ifelse(y==0,0,base:::"/"(x,y))

dyn_pmgsy <- dyn_pmgsy %>% mutate(length = ifelse(is.na(length),0,length), n_roads = ifelse(is.na(n_roads),0,n_roads),cost_km = cost/length, cost_project = cost/n_roads )
```


#### Variable summary {.tabset}


##### Length

```{r}


 
  ggplot(dyn_pmgsy %>% filter(length>0) , aes(length))+
  geom_density(fill = "steelblue")+
    theme_minimal()



```


##### Number of roads

```{r}

 
  ggplot(dyn_pmgsy, aes(n_roads))+
  geom_density(fill = "steelblue")+
    theme_minimal()
```

##### cost per kilometre

```{r}
  ggplot(dyn_pmgsy %>% filter(cost_km>0), aes(cost_km))+
  geom_density(fill = "steelblue")+
    theme_minimal()
```


##### cost per project


```{r}

  ggplot(dyn_pmgsy %>% filter(cost_project>0), aes(cost_project))+
  geom_density(fill = "steelblue")+
    theme_minimal()

#dyn_pmgsy %>% select(cost_km)

```


### Regressions {.tabset}

```{r}

library(lfe)

#summary(fit.length)

fit.length <- felm(length ~dyn_cum_2 + constituency_type +log(electors)+incumbent+no_terms+turnout_percentage+ margin_percentage+enop+nl_tot|year+district_name|0|district_name, data = subset(dyn_pmgsy %>%  filter(length>0)))

#summary(fit.length)



fit.cost_km<- felm(cost_km~dyn_cum_2 + constituency_type +log(electors)+incumbent+no_terms+turnout_percentage+ margin_percentage+enop+nl_tot|year+district_name|0|district_name, data = subset(dyn_pmgsy %>%  filter(cost_km>0)))

#summary(fit.cost_km)



fit.cost_project<- felm(cost_project~dyn_cum_2 + incumbent+no_terms+constituency_type +log(electors)+turnout_percentage+ margin_percentage+enop+nl_tot|year+district_name|0|district_name, data = subset(dyn_pmgsy %>%  filter(cost_project>0)))

#summary(fit.cost_project)

```

#### Linear


```{r results="asis"}

library(stargazer)

 stargazer(fit.length, fit.cost_km, fit.cost_project, title="Linear regression - PMGSY  ",type = "text",
align=TRUE,  no.space=TRUE,omit.stat=c("LL","ser","f"),dep.var.labels = c("road length", "Cost per km", "cost per project"),
add.lines=list(c('Year fixed effects', 'Yes','Yes','Yes' ), c('District fixed effects', 'Yes','Yes','Yes'), c('Clustered error', 'District','District','District')))

```

---

#### Poisson

```{r results="asis"}

library(fixest)

fit.nroad  <- fepois(n_roads ~dyn_cum_2 + constituency_type +log(electors)+incumbent+no_terms+turnout_percentage+ margin_percentage+enop+nl_tot|year+district_name, cluster =~district_name, data = dyn_pmgsy) 


etable(fit.nroad,label = "Number of roads - Poisson", title= "Poisson - Number of roads")%>% kable() %>% kable_styling(full_width = F)

fit.nroad  <- felm(n_roads ~dyn_cum_2 + constituency_type +log(electors)+incumbent+no_terms+turnout_percentage+ margin_percentage+enop+nl_tot|year+district_name|0| district_name, data = dyn_pmgsy) 

stargazer(fit.nroad, type = "text")
```

---
## Panel data

```{r}

pmgsy_ac <- fread("~/work/cpr/data/up_misc/merged_ac_all.csv")

pmgsy_df <- pmgsy_ac %>% select(c(1:1,3:3,124:135)) %>% rename(cost = `Sanction Cost`, length = `Road Length (Kms)` , expenditure = `Expenditure Till Date`) %>% mutate(left_over = cost- expenditure , cost_km = cost/length)



dyn <- fread("~/work/cpr/UP/up-dynasties/dyn_other_data/dyn_ae_ge.csv")

dyn <- dyn %>% filter(year %in% c(2007, 2012)&position ==1&election_type=="AE")

dyn_pmgsy <- inner_join( dyn,pmgsy_df, by = c("year", "constituency_no"))




```


```{r}

fit.length <- felm(cost_km ~dyn_cum_2 + constituency_type +log(electors)+incumbent+no_terms+turnout_percentage+ margin_percentage+enop, data = subset(dyn_pmgsy %>%  filter(length>0 & year ==2007)))

summary(fit.length)



fit.cost_km<- felm(cost_km~dyn_cum_2 + constituency_type +log(electors)+incumbent+no_terms+turnout_percentage+ margin_percentage+enop+nl_tot|year+district_name|0|district_name, data = subset(dyn_pmgsy %>%  filter(cost_km>0)))

#summary(fit.cost_km)



fit.cost_project<- felm(cost_project~dyn_cum_2 + incumbent+no_terms+constituency_type +log(electors)+turnout_percentage+ margin_percentage+enop+nl_tot|year+district_name|0|district_name, data = subset(dyn_pmgsy %>%  filter(cost_project>0)))

#summary(fit.cost_project)

```




---

# PMGSY contractors data 

## Summary {.tabset}

```{r}
raw_data <- readxl::read_xlsx("~/work/cpr/data/up_misc/PMGSY Contractors.xlsx", sheet = 1:1)
```


### Dimension


```{r}

dim(raw_data)

```

### variable names

```{r}
names(raw_data)
```



### Preview

```{r}
DT::datatable(head(raw_data))
```

### Missing caste

`TRUE` represents missing ones

```{r}
table(is.na(raw_data$Caste)) %>% kable(col.names = c("is.na","Count")) %>% kable_styling(full_width = F)
```

### Unique castes

```{r}
unique(raw_data$Caste)
```


### caste distribution








```{r}


raw_data <- raw_data %>% mutate(caste_group = case_when (grepl(c("Brahmin|Thakur|Bania|UC|Kayasth|Bhumihaar|Rajput|Raput|Jaiswal|Jain"), Caste,ignore.case = TRUE )~"UC",
                                             grepl(c("Muslim"), Caste,ignore.case = TRUE)~"Muslims",
                                             grepl(c("SC"), Caste,ignore.case = TRUE)~"Dalit",
                                             grepl(c("Yadav|Kurmi|Maurya|OBC|Jat|Punjabi|Sahu| Khatris|OBC|Lodhi|Kushwaha"), Caste,ignore.case = TRUE )~"OBC",
                                             
                                             
                                             TRUE~ "Un-identified"))

raw_data %>% group_by(caste_group) %>% summarise(count= n(), pc = count/length(raw_data$Caste)*100)  %>% arrange(-count) %>% slice(1:1, 3:5,2:2) %>%kable(digits =0, col.names = c("Caste","Count", "Percentage")) %>%  kable_styling(full_width = F)

#raw_data %>% filter(caste_group=="Un-identified") %>% distinct(Caste)

```





# PWD roads {.tabset}


```{r}
pwd<- fread("~/work/cpr/UP/up-dynasties/dyn_other_data/roads-uppwd.csv", stringsAsFactors = FALSE)

#dyn_cum_2 fam_exp_cum_cat mean(\road length`)`glimpse(pwd)


names(pwd) <- tolower(names(pwd))

names(pwd) <- make.unique(names(pwd))

pwd <- pwd %>% select(`ac no`, everything())%>% select(c(1:11)) %>% rename(constituency_no = `ac no`)

dyn_ae_w <- dyn %>% filter(year == 2017 & election_type == "AE" & position==1)

#dyn_ae_w %>% group_by(constituency_no)


dyn_pwd <- merge(dyn_ae_w,pwd, by = c( "constituency_no"))

dyn_pwd$dyn_cum_2_text <- ifelse(dyn_pwd$dyn_cum_2 ==0, "Non-family","Family")


names(dyn_pwd) <- make.unique(names(dyn_pwd))

#summary(pwd)

dyn_pwd$fam_exp_cum_cat <- factor(dyn_pwd$fam_exp_cum_cat, levels=c("[0,1)","[1,6)","[6,11)","[11,21)","[21,Inf]"))
```

## summary stats

```{r summary stats}

#unique(dyn_pwd$department)

dyn_pwd %>% group_by(year) %>% summarise(count = n(),total_road_len =sum(`road length`), mean_len_proj = total_road_len/count,proj_con =n()/n_distinct(constituency_no), len_con = sum(`road length`)/n_distinct(constituency_no)) %>%  kable(caption = "Summary of PMGSY", col.names = c ("Year", "Number of projects","Total length", "Average road length per project (km)","Average number of projects per constituency","Average road length per constituency (km)"),digits = 1)%>% kable_styling(bootstrap_options = "striped")


```




## Family type



```{r}


dyn_pwd  <- dyn_pwd  %>% group_by(constituency_no) %>% mutate(ac_proj_no = n())


dyn_pwd %>% group_by(dyn_cum_2_text) %>% summarise(sum = sum(`road length`), count = n_distinct(constituency_no),mean_proj_con = n()/count,mean_proj = mean(`road length`), mean_con = sum/count) %>% select(dyn_cum_2_text,mean_proj_con,mean_proj, mean_con) %>% kable(caption = "Average number of projects and length of the road wrt constituency type", col.names = c("Constituency Type","Number of projects","Length per project", "Length over all"),digits = 1)%>% kable_styling(bootstrap_options = "striped")






```







## Experience 






```{r}


dyn_pwd %>% group_by(fam_exp_cum_cat) %>% summarise(proj =n()/n_distinct(constituency_no), len = sum(`road length`)/n_distinct(constituency_no)) %>% select(fam_exp_cum_cat,proj, len) %>% kable(caption = "Average number of projects and length of the road wrt experience category", col.names = c("Experience category","Number of projects","Length over all"),digits = 1)%>% kable_styling(bootstrap_options = "striped")
```


```{r}
dyn_pwd %>% group_by(dyn_cum_2_text,fam_exp_cum_cat) %>% summarise(proj =n()/n_distinct(constituency_no), len = sum(`road length`)/n_distinct(constituency_no)) %>% select(dyn_cum_2_text,fam_exp_cum_cat,proj, len) %>% kable(caption = "Average number of projects and length of the road wrt experience category", col.names = c("Constituency type","Experience category","Number of projects","Length over all"),digits = 1)%>% kable_styling(bootstrap_options = "striped")



```

## caste

```{r}
 dyn_pwd %>% group_by(caste_groups) %>% summarise(proj =n()/n_distinct(constituency_no), len = sum(`road length`)/n_distinct(constituency_no)) %>% arrange(-proj) %>% kable(caption = "PWD road stats wrt to caste groups", col.names = c("Caste group", "Average number of projects", "Average over all road length"), digits = 0) %>% kable_styling(bootstrap_options = "striped")


```

# other page



```{r}


pmgsy <- readxl::read_xlsx("~/work/cpr/data/up_misc/PMGSY Contractors.xlsx")

pmgsy$Caste <- tolower(pmgsy$Caste)

data.frame(prop.table(table(pmgsy$Caste))) %>% arrange(-Freq)%>% rename(caste = Var1, pc = Freq) %>%  kable(digits = 2)
# 
# [5:36 PM, 5/18/2021] Rahul Verma: Non-Yadav OBCs =  kurmi obc lodhi sahu kushwaha mauryaa
# [5:36 PM, 5/18/2021] Rahul Verma: Dalit = SC
# [5:36 PM, 5/18/2021] Rahul Verma: Muslim
# [5:37 PM, 5/18/2021] Rahul Verma: Others

pmgsy <- pmgsy %>% mutate(caste_groups = case_when(Caste %in% c("thakur", "brahmin", "bania", "uc", "rajput", "kyastha", "jat", "jain","jaiswal" ,"raput", "bhumihar" ,"khatris")~ "Upper Caste",
                                             Caste =="yadav"~"Yadav",
                                             Caste %in% c("kurmi", "obc", "lodhi", "sahu", "kushwaha", "mauryaa")~"Non-Yadav OBC",
                                             Caste %in% c("dalit","sc") ~ "Dalit",
                                             Caste == "muslim"~"Muslim",
                                                                                         TRUE~"Others"))

#pmgsy$caste_groups <- ifelse(pmgsy$caste_groups=="NA", NA,pmgsy$caste_groups)




```



```{r}


pmgsy$caste_groups <- factor(pmgsy$caste_groups, levels = c("Upper Caste","Yadav","Non-Yadav OBC","Dalit" ,  ,"Others" ))


pmgsy %>% filter(!is.na(caste_groups)) %>% group_by(caste_groups) %>% summarise(count = n(), pc = count/length(pmgsy$caste_groups)*100) %>% mutate(caste = "caste") %>% 
  ggplot(aes(x= caste, fill = caste_groups, y=pc,label = round(pc,0)))+
      geom_col()+
      geom_text(size = 2.5, position = position_stack(vjust = 0.5))+

    colorspace::scale_fill_discrete_qualitative(palette= "dark3" )+

    theme_minimal()+
  theme(aspect.ratio=4/2)+
labs(title = "Caste composition of PMGSY contractors ",x = "", y = "", fill = "Caste Groups")+
    theme(plot.margin = unit(c(.5,.5,.5,.5), "cm"))+
  theme(plot.background = element_blank(),
        axis.line.x = element_line(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.y = element_blank()
  ) 



```





```{r}
dyn_ae_ge$caste_groups <- factor(dyn_ae_ge$caste_groups, levels = c("Upper Caste","Yadav","Non-Yadav OBC","Dalit" , "Muslim"  ,"Others" ))


dyn_ae_ge %>% filter(dyn_cum_2 ==1) %>% distinct(family_id, .keep_all = TRUE)%>% group_by(caste_groups) %>% summarise(count = n(), prop = count/322 *100)%>% mutate(caste = "caste") %>% 
  ggplot(aes(caste, prop, fill = caste_groups, label = round(prop,0)))+
    geom_col()+
      geom_text(size = 2.5, position = position_stack(vjust = 0.5))+

    colorspace::scale_fill_discrete_qualitative(palette= "dark3" )+

    theme_minimal()+
  theme(aspect.ratio=4/2)+
labs(title = "Caste composition of families ",x = "", y = "", fill = "Caste Groups")+
    theme(plot.margin = unit(c(.5,.5,.5,.5), "cm"))+
  theme(plot.background = element_blank(),
        axis.line.x = element_line(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.y = element_blank()
  ) 

```


