---
title: "UP Dynasties extended"
author: ""
date: "2020-08-09"
params:
  orig_date: "Original Publish Date: 09 August, 2020"
  update_date: !r paste("Updated on:", format(Sys.time(), '%d %B, %Y'))
output:
  html_document:
    theme: readable
    toc: TRUE
    toc_float: TRUE
    toc_depth: 5
    number_sections: false
    fig_width: 6            
editor_options: 
  chunk_output_type: inline

---

---

### Document History

`r params$orig_date`

`r params$update_date`

---

```{r set up, warning=FALSE, include=FALSE, message= FALSE}

knitr::opts_chunk$set(cache = FALSE,echo = FALSE, message=FALSE, warning = FALSE,fig.width = 16/2, fig.height = 9/2)


library(tidyverse)
library(data.table)
library(knitr)
library(kableExtra)
library(scales)
library(gridExtra)
library(stargazer)
library(ggbump)
`%!in%` = Negate(`%in%`)

select <- dplyr::select
```

We will be using the dynasties data for last few elections from UP in this post.

# GE {.tabset}

```{r reading ge file}


ge_5pc <- read.csv("D:/cpr/UP/up-dynasties/dyn_other_data/dyn_ge_5pc_up_09_19.csv")

#filter out by polls


names(ge_5pc) <- tolower(names(ge_5pc))



#names(ge_5pc)[1] <- "state_name"

ge_5pc <- ge_5pc %>% select(state_name, year,constituency_no,position, jati, caste_rec, dyn, source,background.dynasty, notes)

## reading tcpd file

tcpd_ge_all <- read.csv("D:/cpr/UP/up-dynasties/dyn_other_data/TCPD_GE_all_2020-7-2.csv")

names(tcpd_ge_all) <- tolower(names(tcpd_ge_all))

# ge_5pc <- merge(ge_5pc, tcpd_ge_all, by = c("state_name", "year", "constituency_no", "position"))

ge_5pc <- inner_join(ge_5pc, tcpd_ge_all, by = c("state_name", "year", "constituency_no", "position"))

ge_5pc$dynast <- ifelse(ge_5pc$dyn ==1, "Dynast", "Non-Dynast")


ge_5pc <- ge_5pc %>% filter(position <=3)
```

```{r merging the dynasty data with enumerator one}
# 
# dyn_ae_ge <- read.csv("D:/cpr/UP/up-dynasties/dyn_other_data/dyn_ae_ge.csv")
# 
# 
# dyn_ae_dyn <- dyn_ae_ge %>% filter(year >2010 & election_type == "AE") %>% select(year, constituency_no, position, dyn_cum_2)
# 
# 
# dyn_ae_5pc <- left_join(ae_5pc, dyn_ae_dyn, by = c("year", "constituency_no", "position"))
# 
# write.csv(dyn_ae_5pc, "D:/cpr/UP/up-dynasties/dyn_other_data/dyn_ae_5pc_up_09_19.csv")


```


### Basic summary of the data

Type of election - General elections

State - Uttar Pradesh

Year - 2009:20019

at 5% percentage vote share

  - Number of observations - 787

  - Average vote share percentage - `r round(mean(ge_5pc$vote_share_percentage))`%

  - Distribution of the positions - 
  
```{r}
round(prop.table(table(ge_5pc$position)),2)

```
  
  
  - Proportion of dynasts in the data - `r data.frame(round(prop.table(table(ge_5pc$dyn)),2))[2,2]`


### Dynasts {.tabset}


#### Proportion of positions won by dynast candidates


```{r}

ge_5pc %>%  group_by(dynast, position) %>% summarise(count = n() ) %>% group_by(,position) %>% mutate(sum= sum(count), prop = count/sum) %>% filter(dynast == "Dynast") %>%reshape2::dcast(position  ~ dynast) %>% kable(digits = 2) %>% kable_styling(full_width = F)

```

---

<!-- ```{r eda} -->
<!-- ge_5pc %>%  group_by(year,dynast, position) %>% summarise(count = n() ) %>% group_by(year,position) %>% mutate(sum= sum(count), prop = count/sum) %>% filter(dynast == "Dynast") %>%reshape2::dcast(position  ~ year) %>% replace(is.na(.),0)%>% kable(digits = 2) %>% kable_styling(full_width = F) -->


<!-- ``` -->

---

####  By position

```{r}
ge_5pc %>% group_by(dynast, position) %>% summarise(count = n() ) %>% group_by(dynast) %>% mutate(sum= sum(count), prop = count/sum) %>% reshape2::dcast(dynast  ~position) %>% kable(digits = 2) %>% kable_styling(full_width = F)
```

---



<!--  ```{r} -->
<!--  ge_5pc %>%  group_by(year,dynast, position) %>% summarise(count = n() ) %>% group_by(year,dynast) %>% mutate(sum= sum(count), prop = count/sum) %>% filter(dynast == "Dynast") %>%reshape2::dcast(year  ~ position) %>% replace(is.na(.),0)%>% kable(digits = 2) %>% kable_styling(full_width = F) -->


<!-- ``` -->


---

<!-- #### **Vote Share** -->

<!-- ```{r} -->

<!-- ge_5pc %>% group_by(dynast) %>%summarise(mean_vote_share = mean(vote_share_percentage)) %>% kable(digits = 0) %>% kable_styling(full_width = F) -->

<!-- ``` -->

<!-- --- -->

<!-- ```{r} -->
<!-- ge_5pc %>%  group_by(position,dynast) %>%  summarise(mean_vote_share = mean(vote_share_percentage))  %>%reshape2::dcast(dynast  ~ position) %>% replace(is.na(.),0)%>% kable(digits = 0) %>% kable_styling(full_width = F) -->

<!-- ``` -->


---



### Turncoats {.tabset}

#### Turncoats proportion wrt Politicians identity

```{r}

ge_5pc%>%  group_by(dynast) %>% summarise(mean_turncoat = mean(turncoat)) %>% kable( digit = 2)  %>% kable_styling(full_width = F)


```




#### by posiiton

```{r}
ge_5pc %>%  group_by(position,dynast) %>%  summarise(mean_turncoat = mean(turncoat))  %>%reshape2::dcast(dynast  ~ position) %>% replace(is.na(.),0)%>% kable(digits = 2) %>% kable_styling(full_width = F)

```

---

### Same party {.tabset}


#### Party retention wrt Politicians identity

```{r}

ge_5pc%>%  group_by(dynast) %>% summarise(mean_same_party = mean(same_party, na.rm = TRUE)) %>% kable( digit = 2)  %>% kable_styling(full_width = F)


```

#### Position

```{r}
ge_5pc %>%  group_by(position,dynast) %>%  summarise(mean_turncoat =mean(same_party, na.rm = TRUE))  %>%reshape2::dcast(dynast  ~ position) %>% replace(is.na(.),0)%>% kable(digits = 2) %>% kable_styling(full_width = F)
```

---


### Incumbents {.tabset}



#### Proportion of incumbents wrt Politicians identity

```{r}

ge_5pc%>%  group_by(dynast) %>% summarise(mean_incumbent = mean(incumbent, na.rm = TRUE)) %>% kable( digit = 2)  %>% kable_styling(full_width = F)



```



#### By position

```{r}

ge_5pc %>%  group_by(year,dynast) %>%  summarise(mean_incumbent = mean(incumbent, na.rm = TRUE))  %>%reshape2::dcast(dynast  ~ year) %>% replace(is.na(.),0)%>% kable(digits = 2) %>% kable_styling(full_width = F)

```


---

### Recontest {.tabset}

#### Proportion of re-contestants wrt Politicians identity


```{r}

ge_5pc%>%  group_by(dynast) %>% summarise(mean_recontest = mean(recontest, na.rm = TRUE)) %>% kable( digit = 2)  %>% kable_styling(full_width = F)

```


---
```{r}

ge_5pc %>%  group_by(position,dynast) %>%  summarise(mean_recontest = mean(recontest, na.rm = TRUE))  %>%reshape2::dcast(dynast  ~ position) %>% replace(is.na(.),0)%>% kable(digits = 2) %>% kable_styling(full_width = F)

```

---


### Number of terms {.tabset}

#### Number of terms wrt Politicians identity

```{r}

ge_5pc%>%  group_by(dynast) %>% summarise(mean_no_terms = mean(no_terms, na.rm = TRUE)) %>% kable( digit = 2)  %>% kable_styling(full_width = F)


```

#### By posiiton

```{r}
ge_5pc %>%  group_by(year,dynast) %>%  summarise(mean_no_terms = mean(no_terms, na.rm = TRUE))  %>%reshape2::dcast(dynast  ~ year) %>% replace(is.na(.),0)%>% kable(digits = 2) %>% kable_styling(full_width = F)
```

---


### Constituency type {.tabset}

#### Constituency type wrt Politicians identity


```{r}

ge_5pc%>%  group_by(dynast, constituency_type) %>% summarise(count  = n()) %>% group_by(dynast) %>% mutate(sum = sum(count), prop = count/sum) %>% reshape2::dcast(dynast ~ constituency_type) %>% kable(digits = 2) %>% kable_styling(full_width = F)


```

#### By position


```{r}
ge_5pc%>%  group_by(year,dynast, constituency_type) %>% summarise(count  = n()) %>% group_by(dynast,year) %>% mutate(sum = sum(count), prop = count/sum) %>% reshape2::dcast(year +dynast  ~ constituency_type) %>% kable(digits = 2) %>% kable_styling(full_width = F)


```





---

# AE {.tabset}
  
  
```{r reading ae file}

ae_5pc <-  read.csv("D:/cpr/UP/up-dynasties/dyn_other_data/dyn_ae_5pc_up_09_19.csv")

names(ae_5pc) <- tolower(names(ae_5pc))

ae_5pc <- ae_5pc %>% filter(poll_no ==0 )

ae_5pc$dynast <- ifelse(ae_5pc$dyn ==1, "Dynast", "Non-Dynast")

ae_5pc <- ae_5pc %>% filter(position <=3)

```



### Basic summary of the data

Type of election - Assembly elections

State - Uttar Pradesh

at 5% percentage vote share

  - Number of observations - 2960

  - Average vote share percentage - `r round(mean(ae_5pc$vote_share_percentage),2)`

  - Distribution of the positions -
  
```{r}

round(prop.table(table(ae_5pc$position)),2)

```


- Proportion of dynasts - `r data.frame(round(prop.table(table(ae_5pc$dyn)),2))[2,2]`

---

### Dynasts {.tabset}


#### Proportion of positions won by dynast candidates


```{r}

ae_5pc %>%  group_by(dynast, position) %>% summarise(count = n() ) %>% group_by(,position) %>% mutate(sum= sum(count), prop = count/sum) %>% filter(dynast == "Dynast") %>%reshape2::dcast(position  ~ dynast) %>% kable(digits = 2) %>% kable_styling(full_width = F)

```

<!-- --- -->

<!-- #### By position -->

<!-- ```{r } -->
<!-- ae_5pc %>%  group_by(year,dynast, position) %>% summarise(count = n() ) %>% group_by(year,position) %>% mutate(sum= sum(count), prop = count/sum) %>% filter(dynast == "Dynast") %>%reshape2::dcast(position  ~ year) %>% replace(is.na(.),0)%>% kable(digits = 2) %>% kable_styling(full_width = F) -->


<!-- ``` -->

---

#### By position

```{r}
ae_5pc %>% group_by(dynast, position) %>% summarise(count = n() ) %>% group_by(dynast) %>% mutate(sum= sum(count), prop = count/sum) %>% reshape2::dcast(dynast  ~position) %>% kable(digits = 2) %>% kable_styling(full_width = F)
```

---

<!-- ```{r} -->
<!-- ae_5pc %>%  group_by(year,dynast, position) %>% summarise(count = n() ) %>% group_by(year,dynast) %>% mutate(sum= sum(count), prop = count/sum) %>% filter(dynast == "Dynast") %>%reshape2::dcast(year  ~ position) %>% replace(is.na(.),0)%>% kable(digits = 2) %>% kable_styling(full_width = F) -->


<!-- ``` -->


---

<!-- **Vote Share** -->

<!-- ```{r} -->

<!-- ae_5pc %>% group_by(dynast) %>%summarise(mean_vote_share = mean(vote_share_percentage)) %>% kable(digits = 0) %>% kable_styling(full_width = F) -->

<!-- ``` -->

<!-- --- -->

<!-- ```{r} -->
<!-- ae_5pc %>%  group_by(year,dynast) %>%  summarise(mean_vote_share = mean(vote_share_percentage))  %>%reshape2::dcast(dynast  ~ year) %>% replace(is.na(.),0)%>% kable(digits = 0) %>% kable_styling(full_width = F) -->

<!-- ``` -->


---

### Turncoat {.tabset}

#### Turncoats proportion wrt Politicians identity

```{r}

ae_5pc%>%  group_by(dynast) %>% summarise(mean_turncoat = mean(turncoat)) %>% kable( digit = 2)  %>% kable_styling(full_width = F)


```


#### By position

```{r}
ae_5pc %>%  group_by(position,dynast) %>%  summarise(mean_turncoat = mean(turncoat))  %>%reshape2::dcast(dynast  ~ position) %>% replace(is.na(.),0)%>% kable(digits = 2) %>% kable_styling(full_width = F)

```

---

### Same Party {.tabset}



#### Party retention wrt Politicians identity

```{r}

ae_5pc%>%  group_by(dynast) %>% summarise(mean_same_party = mean(same_party, na.rm = TRUE)) %>% kable( digit = 2)  %>% kable_styling(full_width = F)


```

#### By position


```{r}
ae_5pc %>%  group_by(position, dynast) %>%  summarise(mean_turncoat =mean(same_party, na.rm = TRUE))  %>%reshape2::dcast(dynast  ~ position) %>% replace(is.na(.),0)%>% kable(digits = 2) %>% kable_styling(full_width = F)
```

---


### Incumbency {.tabset}


#### Proportion of incumbents wrt Politicians identity

```{r}

ae_5pc%>%  group_by(dynast) %>% summarise(mean_incumbent = mean(incumbent, na.rm = TRUE)) %>% kable( digit = 2)  %>% kable_styling(full_width = F)



```

#### By position

```{r}

ae_5pc %>%  group_by(position,dynast) %>%  summarise(mean_incumbent = mean(incumbent, na.rm = TRUE))  %>%reshape2::dcast(dynast  ~ position) %>% replace(is.na(.),0)%>% kable(digits = 2) %>% kable_styling(full_width = F)

```


---

### Recontest {.tabset}


#### Proportion of re-contestants wrt Politicians identity


```{r}

ae_5pc%>%  group_by(dynast) %>% summarise(mean_recontest = mean(recontest, na.rm = TRUE)) %>% kable( digit = 2)  %>% kable_styling(full_width = F)

```



#### By position


```{r}

ae_5pc %>%  group_by(position,dynast) %>%  summarise(mean_recontest = mean(recontest, na.rm = TRUE))  %>%reshape2::dcast(dynast  ~ position) %>% replace(is.na(.),0)%>% kable(digits = 2) %>% kable_styling(full_width = F)

```

---

### Number of terms {.tabset}

#### Number of terms wrt Politicians identity

```{r}

ae_5pc%>%  group_by(dynast) %>% summarise(mean_no_terms = mean(no_terms, na.rm = TRUE)) %>% kable( digit = 2)  %>% kable_styling(full_width = F)


```

#### By position

```{r}
ae_5pc %>%  group_by(dynast,position) %>%  summarise(mean_no_terms = mean(no_terms, na.rm = TRUE))  %>%reshape2::dcast(dynast  ~ position) %>% replace(is.na(.),0)%>% kable(digits = 2) %>% kable_styling(full_width = F)
```



### Constituency type {.tabset}

#### Constituency type wrt Politicians identity


```{r}


ae_5pc%>%  group_by(dynast, constituency_type) %>% summarise(count  = n()) %>% group_by(dynast) %>% mutate(sum = sum(count), prop = count/sum) %>% reshape2::dcast(dynast ~ constituency_type) %>% kable(digits = 2) %>% kable_styling(full_width = F)


```

#### By position

```{r}
ae_5pc%>%  group_by(position,dynast, constituency_type) %>% summarise(count  = n()) %>% group_by(dynast,position) %>% mutate(sum = sum(count), prop = count/sum) %>% reshape2::dcast(position +dynast  ~ constituency_type) %>% kable(digits = 2) %>% kable_styling(full_width = F)


```




