---
title: "Tamil Nadu Analysis - 1"
author: "Najah"
date: "19/03/2021"
params:
  orig_date: 'Original Publish Date: 19 March, 2020'
  update_date: !r paste("Updated on:", format(Sys.time(), '%d %B, %Y'))
output:
  html_document:
    theme: flatly
    toc: TRUE
    toc_float: TRUE
    toc_depth: 4
    number_sections: false
    fig_width: 6            
editor_options: 
  chunk_output_type: inline
---

```{=html}
<style>
    body .main-container {
        max-width: 1000px;
    }
</style>
```

------------------------------------------------------------------------

### Document History

`r params$orig_date`

`r params$update_date`

------------------------------------------------------------------------

```{r set up, warning=FALSE, include=FALSE, message= FALSE }

knitr::opts_chunk$set(cache = FALSE ,echo = FALSE, message=FALSE, warning = FALSE,fig.width = 16/2, fig.height = 9/2)

library(data.table)
library(tidyverse)
library(kableExtra)
library(cowplot)

`%!in%` = Negate(`%in%`)

select <- dplyr::select
```




```{r}


## reading AE files


tn_ae <- fread("D:/cpr/data/tcpd/states/Tamil_Nadu_2020.csv")

names(tn_ae) <- tolower(names(tn_ae))



## reading pc files

ac_19 <- readxl::read_xls("D:/cpr/data/GE_PC_AC-main/2019_AC_PC.xls")



tn_19 <- ac_19 %>% filter(`State-UT Code & Name` == "Tamil Nadu" ) %>% ungroup()

names(tn_19) <- tolower(names(tn_19))




tn_19 <- tn_19 %>% rename(state_name = `state-ut code & name`, pc_no = `pc no` , pc_name = `pc name`, constituency_no = `ac no`, constituency_name = `ac name`, electors = `total electors`, candidate = `candidate name`,votes = `votes secured evm`)

tn_19<- tn_19 %>% group_by(year, constituency_no) %>% mutate(election_type = "GE",valid_votes=sum(votes, na.rm = TRUE), vote_share_percentage =( votes/valid_votes)*100,
                                                                   turnout_percentage = (valid_votes/electors)*100) %>% ungroup()

 tn_19  <- tn_19  %>% group_by(year, constituency_no) %>%  mutate(position = order(order(vote_share_percentage, decreasing=TRUE))) %>% ungroup()

``` 
 
```{r}


# ac_14 <-  readxl::read_xlsx("D:/cpr/data/GE_PC_AC-main/2014_AC_PC.xlsx")
# 
# tn_14 <- ac_14 %>% filter(`State-UT Code & Name` == "Tamil Nadu" )
# 
# names(tn_14) <- tolower(names(tn_14))
# 
# 
# 
# tn_14 <- tn_14 %>% rename(state_name = `state-ut code & name`, pc_no = pcno, pc_name = `pc name`, constituency_no = `ac no`, constituency_name = `ac name`, electors = `total electors in ac`, candidate = `candidate name`,votes = `votessecured evm`)
# 
# 
# tn_14<- tn_14 %>% group_by(year, constituency_no) %>% mutate(election_type = "GE",valid_votes=sum(votes, na.rm = TRUE), vote_share_percentage =( votes/valid_votes)*100,
#                                                                    turnout_percentage = (valid_votes/electors)*100) %>% ungroup()
# 
#  tn_14  <- tn_14  %>% group_by(year, constituency_no) %>%  mutate(position = order(order(vote_share_percentage, decreasing=TRUE))) %>% ungroup()
#  
# #  
#  unique (tn_14$party)
# # 
# # unique (tn_14$front[tn_14$position%in% c(1,2)])
# 
# tn_14 <- tn_14 %>% mutate(front = case_when(party %in% c("ADMK") ~"ADMK",
#                                   party %in% c("DMK","IUML","MAMAK","VCK","PT")~"DMK front",
#                                    
#                                    party %in% c("BJP","PMK","DMDK" ) ~"NDA",
#                                   party %in% c("CPI", "CPIM") ~"LEFT",
#                                   party =="INC"~ "UPA",
#                  TRUE ~ "OTHERS"))

# tn_14  %>% filter(position ==1 & party == "IND" & front%!in% c("NDA","LDF","UDF"))
# #tn_14 %>% filter(grepl("peelipose", candidate, ignore.case = TRUE))
# 
# 
# tn_14_19 <- rbindlist(list(tn_14,tn_19), use.names = FALSE)
```

```{r}



tn_19 <- tn_19 %>% mutate(front = case_when(party %in% c("INC","DMK","CPI","CPIM","IUML","VCK" ) ~"UPA",
                                   party %in% c("ADMK", "PMK", "BJP","DMDK","TMC(M)" ) ~"NDA",
                 TRUE ~ "OTHERS"))



tn_19 <- tn_19 %>% ungroup() %>%  mutate(votes_state = sum(votes))
#
```


# 2019 GE



## Results{.tabset}


### Vote share - front


```{r}


tn_19 %>%ungroup() %>%  group_by(front) %>% summarise(vs = (sum(votes)/votes_state)*100 ) %>% distinct(front,.keep_all = TRUE) %>% kable(digits = 2, caption = "vote share in the state - GE 2019") %>% kable_styling(bootstrap_options = "striped")

```



---

### Vote share - party


```{r}


tn_19 %>%ungroup() %>%  group_by(front,party) %>% summarise(vs = (sum(votes)/votes_state)*100 ) %>% distinct(party,.keep_all = TRUE) %>% filter(vs>2)%>%arrange(front,-vs) %>% kable(digits = 2, caption = "vote share in the state - GE 2019") %>% kable_styling(bootstrap_options = "striped")

```

---


### Seat share - Front


```{r}
tn_19 %>% ungroup() %>% filter(position ==1) %>% group_by(front) %>% summarise(n_ac = n()) %>% kable(digits = 2, caption = "Leading ACs - GE 2019") %>% kable_styling(bootstrap_options = "striped")

```

---

### Seat share - Party


```{r}
tn_19 %>% ungroup() %>% filter(position ==1) %>% group_by(party) %>% summarise(n_ac = n()) %>% arrange(-n_ac)%>% kable(digits = 2, caption = "Leading ACs - GE 2019") %>% kable_styling(bootstrap_options = "striped")
```




## Sub-region{.tabset}


```{r}

sub_reg <- read.csv("D:/cpr/elections/tn/sub_region.csv")

names(sub_reg) <- tolower(names(sub_reg))


#names(sub_reg)[1] <- "constituency_no"

sub_reg %>% group_by(sub_reg_1) %>% summarise(count = n()) %>% kable() %>% kable_styling(bootstrap_options ="striped" )


# dt_table <- sub_reg %>% distinct(district_name, .keep_all = TRUE) %>% select(district_name, sub_reg_1) %>% arrange(sub_reg_1) %>% as.data.table()
# 
# write.csv(dt_table, "D:/cpr/elections/TN/districts.csv")



```



---


|  Sub Region               	| n_ac 	| Districts                                                                                              	|
|-----------------	|------	|--------------------------------------------------------------------------------------------------------	|
| Upper   North   	| 42   	| TIRUVALLUR, CHENNAI,   KANCHIPURAM, VELLORE, KRISHNAGIRI                                               	|
| North   Central 	| 54   	| DHARMAPURI, SALEM,   TIRUVANNAMALAIVILLUPURAM, CUDDALORE                                               	|
| Cauvery   Delta 	| 42   	| KARUR, KARUR, TIRUCHIRAPPALLI,   PUDUKKOTTAI, PERAMBALUR, ARIYALUR, NAGAPATTINAM, THANJAVUR, TIRUVARUR 	|
| West            	| 42   	| NAMAKKAL, ERODE, TIRUPUR,   NILGIRIS, COIMBATORE, DINDIGUL                                             	|
| South           	| 54   	| SIVAGANGA, MADURAI, THENI,   VIRUDHUNAGAR, RAMANATHAPURAM, THOOTHUKUDI, TIRUNELVELI, KANNIYAKUMARI     	|


---

```{r}
tn_19 <- tn_19 %>% inner_join(sub_reg, by = "constituency_no")

tn_19 <- tn_19 %>% group_by(election_type, year, sub_reg_1) %>% mutate(votes_reg = sum(votes))



```

### Vote share

```{r}

tn_19 %>%filter(front %in% c("UPA","NDA")) %>% group_by(year,sub_reg_1, front) %>% summarise(vs = sum(votes)/votes_reg*100)%>%distinct(year, sub_reg_1, front, .keep_all=TRUE) %>% 
  ggplot(aes(factor(sub_reg_1, levels = c("Upper North","North Central", "Cauvery Delta","West","South")),vs, fill = factor(front), label = round(vs, 0) ))+
  geom_bar(stat = "identity",position = "stack")+
  geom_text(position= position_stack(vjust = .5), size = 3)+
 scale_x_discrete(labels= c("Upper \n North","North \n Central", "Cauvery \n Delta","West","South"))+
    scale_fill_manual(values = c(
                                "UPA" = "steelblue",
                             
                                "NDA" = "darkorange1"),
                      labels = c( "ADMK Front","DMK Front"))+
labs(title = "Sub-region wise vote share of major fronts",subtitle = "2019 GE",  x = "Sub-region", y = "Vote share (%)", fill = "Election Type" )+
  

  theme_minimal()+
  
  theme(aspect.ratio = 1,
        plot.background = element_blank(),
      
         legend.title = element_blank(),
           
        axis.ticks = element_blank(),
        panel.grid.major = element_line(),
        panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
      
        axis.line.x = element_line(),
        axis.title.x = element_blank()
       #axis.text.y = element_blank()
  )  +
  ylim(0,100)

ggsave("D:/cpr/elections/TN/front_19_vs.png", width = 6, height = 4)

```



### Seat share

```{r}

tn_19 %>%filter( position==1) %>% group_by(year,sub_reg_1, front) %>% summarise(count = n())%>% 
  ggplot(aes(factor(sub_reg_1, levels =  c("Upper North","North Central", "Cauvery Delta","West","South")),count, fill = factor(front), label = round(count, 0) ))+
  geom_bar(stat = "identity",position = "fill")+
  geom_text(position= position_fill(vjust = .5), size = 3)+
scale_x_discrete(labels= c("Upper \n North","North \n Central", "Cauvery \n Delta","West","South"))+
    scale_fill_manual(values = c(
                                "UPA" = "steelblue",
                             
                                "NDA" = "darkorange1"),
                      labels = c("ADMK Front","DMK Front"))+
labs(title = "Sub-region wise leading seats",subtitle = "2019 GE",  x = "Sub-region", y = "N_seats", fill = "Election Type" )+
  

  theme_minimal()+
  
  theme(aspect.ratio = 1,
        plot.background = element_blank(),
      
         legend.title = element_blank(),
           
        axis.ticks = element_blank(),
        panel.grid.major = element_line(),
        panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
      
        axis.line.x = element_line(),
        axis.title.x = element_blank(),
       axis.text.y = element_blank()
  )  
ggsave("D:/cpr/elections/TN/front_19_seats.png", width = 6, height = 4)

```



# Spatial distribution{.tabset}







```{r results = 'hide'}
library(sf)

ac_shp <- st_read("D:/cpr/data/shape-file/maps-master/assembly-constituencies/India_AC.shp",quiet = TRUE)

#unique(ac_shp$ST_NAME)

ac_tn <- ac_shp %>% filter(ST_NAME == "TAMIL NADU")

party_19 <-  tn_19%>% filter( position %in% c(1,2) ) %>% ungroup()%>% select(constituency_no, position,party) 

party_19_ac <- inner_join(ac_tn, party_19, by = c("AC_NO"= "constituency_no"))
```




## sub_region


```{r}


subreg_map <- inner_join(ac_tn, sub_reg, by = c("AC_NO"= "constituency_no"))

ggplot(subreg_map)+
  geom_sf(aes(fill= factor(sub_reg_1)))+
  colorspace::scale_fill_discrete_qualitative(palette= "Cold")+
      theme_map()+
    #labs(title ="Tamil Nadu : Sub Regions")+
    theme(text = element_text(family = "serif"),
          #legend.position = "bottom",
          legend.title = element_blank())


ggsave("D:/cpr/elections/TN/tn_subreg_map.png", height = 4, width = 6)

```


## Seats won

```{r results = 'hide'}
ggplot(party_19_ac)+
  geom_sf(aes(fill= factor(party, level = c("INC",
                               "DMK"  , 
                               "CPI",
                               "CPIM",
                               "IUML" ,
                               "VCK" ,
                               "ADMK" , 
                               "PMK" , 
                               "BJP" ,
                               "DMDK" ,
                               "TMC(M)"  ,
                               "IND" ,
                               "MNM" ))), lwd = .7)+
  facet_wrap(~position)+
  scale_fill_manual(values = c("INC" = "skyblue",
                               "DMK" ="steelblue" , 
                               "CPI" = "royalblue",
                               "CPIM" = "royalblue",
                               "IUML" = "dodgerblue",
                               "VCK" = "steelblue4",
                               "ADMK" = "orangered", 
                               "PMK" = "orange", 
                               "BJP" = "darkorange1",
                               "DMDK" = "orange3",
                               "TMC(M)"  = "darkorange2",
                               "IND" = "grey",
                               "MNM" = "green"
    
                               ))+
    theme_map()+
    labs(title ="Assembly segments: first and second lead", subtitle = "GE 2019", fill = "Party")+
    theme(text = element_text(family = "serif"),
         # legend.position = "bottom",
          legend.title = element_blank(),)

ggsave("D:/cpr/elections/TN/won_map_19.png", width = 6, height = 4)


```


<!-- ## 2016 -->



<!-- ```{r} -->
<!-- ae_tn_win <- ae_tn %>% filter(position==1) -->

<!-- ae_16_map<- inner_join(ac_tn, ae_tn_win, by = c("AC_NO"= "constituency_no")) -->


<!-- ggplot(ae_16_map %>% filter(year ==2016))+ -->
<!--   geom_sf(aes(fill = party))+ -->




<!-- ``` -->




## Reservation


```{r}
res <-  tn_ae%>% filter(year==2011 & position==1) %>% select(constituency_no, constituency_type) %>% mutate(reservation = ifelse(constituency_type =="GEN","GEN", "SC/ST")) 

table(res$reservation)
```


## Vote share correlation


### Turnout


```{r}

pc_to <- readxl::read_xls("D:/cpr/data/election/2019/pc_turnnout_19.xls")

pc_to_tn <- pc_to %>% filter(`State Name` == "Tamil Nadu")


tn_19_to <-  tn_19 %>% group_by(pc_no.x, front)%>%summarise(vs = mean(vote_share_percentage)) %>% inner_join(pc_to_tn, by = c("pc_no.x"= "PC NO.")) %>% ungroup() 


ggplot(tn_19_to %>% filter(front != "OTHERS"), aes(FEMALE_to,vs, color = front))+
  geom_point(alpha = .5)+
  geom_smooth(method = "lm", se = FALSE)+
      scale_color_manual(values = c(
                                "UPA" = "steelblue",
                             
                                "NDA" = "darkorange1"))+
     labs(title = "Front vote share as a function of women turnout % ", y = "Vote share(%)",subtitle = "Tamil Nadu General election 2019", x = "Female turnout (%) ", color = "Front")+
    theme_minimal()+
  theme(plot.margin = unit(c(.5,.5,.5,.5), "cm"),
        #legend.position = "bottom",
        plot.background = element_blank(),
        #plot.title = element_text( size = 18, family = "serif"),
        plot.subtitle = element_text(  margin = margin(t = 0, r = 0, b = 20, l = 0)),
     
        axis.ticks = element_blank(),
        panel.grid.major = element_line(color = "gray", size = .5),
        panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
       axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        axis.line.x = element_line(),
        #axis.title.x = element_blank()
  )
  

```








```{r}
tn_19_res <- tn_19 %>% inner_join(res, by = c("constituency_no")) %>% ungroup()



tn_19_res %>% filter(front!= "OTHERS") %>% group_by(reservation,front) %>% summarise(mean_vs = mean(vote_share_percentage)) %>% pivot_wider(values_from = mean_vs, names_from=front) %>% kable(digits = 2, caption = "Average vote share in wrt cosntituency type") %>% kable_styling(bootstrap_options = "striped")

```


```{r profile}


tn_profile <- readxl::read_xls("D:/cpr/elections/TN/tn_ac_profile.xls")

tn_19 <- tn_19 %>% inner_join(tn_profile, by = "constituency_no")


```


### Urban


```{r }

ggplot(tn_19 %>% filter(front != "OTHERS"), aes(    urban,vote_share_percentage, color = front))+
  geom_point(alpha = .5)+
  geom_smooth(method = "lm", se = FALSE)+
      scale_color_manual(values = c("UPA" = "steelblue",
                             
                                "NDA" = "darkorange1"))+
     labs(title = "Front vote share as a function of urban constituencts  ", y = "Vote share(%)",subtitle = "Tamil Nadu General election 2019", x = "Urban (%) ", color = "Front")+
    theme_minimal()+
  theme(plot.margin = unit(c(.5,.5,.5,.5), "cm"),
        #legend.position = "bottom",
        plot.background = element_blank(),
        #plot.title = element_text( size = 18, family = "serif"),
        plot.subtitle = element_text(  margin = margin(t = 0, r = 0, b = 20, l = 0)),
     
        axis.ticks = element_blank(),
        panel.grid.major = element_line(color = "gray", size = .5),
        panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
       axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        axis.line.x = element_line(),
        #axis.title.x = element_blank()
  )

```


### SC Voters


```{r}

ggplot(tn_19 %>% filter(front != "OTHERS"), aes(    sc,vote_share_percentage, color = front))+
  geom_point(alpha = .5)+
  geom_smooth(method = "lm", se = FALSE)+
      scale_color_manual(values = c("UPA" = "steelblue",
                             
                                "NDA" = "darkorange1"))+
     labs(title = "Front vote share as a function of SC constituencts  ", y = "Vote share(%)",subtitle = "Tamil Nadu General election 2019", x = "SC (%) ", color = "Front")+
    theme_minimal()+
  lims(x= c(0,50), y =c(0,80))+
  theme(plot.margin = unit(c(.5,.5,.5,.5), "cm"),
        #legend.position = "bottom",
        plot.background = element_blank(),
        #plot.title = element_text( size = 18, family = "serif"),
        plot.subtitle = element_text(  margin = margin(t = 0, r = 0, b = 20, l = 0)),
     
        axis.ticks = element_blank(),
        panel.grid.major = element_line(color = "gray", size = .5),
        panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
       axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        axis.line.x = element_line(),
        #axis.title.x = element_blank()
  )

```


# Post 2010


```{r}

ae_tn <-read_csv("D:/cpr/data/tcpd/states/Tamil_Nadu_2020.csv")

names(ae_tn)[1] <- "Election_Type"

#ae_ge_kl <- rbind(ge_kl, ae_kl, use.names = TRUE, fill  = TRUE)


names(ae_tn) <- tolower(names(ae_tn) )

ae_tn<-  ae_tn %>% filter(poll_no ==0 & party != "NOTA" & year %in% c(2011,2016))


 #unique(ae_tn$party[ae_tn$position%in% c(1,2,3,4) &ae_tn$year==2016 ])

```






<!-- fronts -->


```{r}

ae_tn<- ae_tn %>% mutate(front = case_when(party %in% c("AIADMK", "ADMK") & year ==2016 ~"ADMK",
                 party %in% c ("DMK","PMK", "INC", "IUML", "MAMAK","PT")& year ==2016~"DMK",
                 party %in% c("BJP", "MDMK") & year ==2016 ~ "NDA",
                 party %in% c("CPI","CPIM", "DMDK","TMC(M)", "VCK", "DMDK") & year ==2016~ "LF",
                 
                 party %in% c("AIADMK", "ADMK","DMDK","CPI","CPIM","PT","DMDK") & year ==2011 ~"ADMK",
                 party %in% c ("DMK","PMK", "INC","VCK", "IUML", "MAMAK")& year ==2011~"DMK",
                 party %in% c("BJP") & year ==2011 ~ "NDA",
                 TRUE ~ "OTHERS"))



```



## vote share


```{r}

ae_tn %>% filter(front %in% c("DMK","ADMK"))%>% group_by(year, front) %>% summarise(mean_vs = mean(vote_share_percentage, na.rm =TRUE)) %>% pivot_wider(values_from = mean_vs, names_from = front) %>% kable(digits = 2) %>% kable_styling(bootstrap_options = "striped")

```

## seat share


```{r}

ae_tn %>%filter(position ==1) %>% filter(front %in% c("DMK","ADMK"))%>% group_by(year, front) %>% summarise(count = n(), pc_seat = count/234*100) %>% kable(digits = 0) %>% kable_styling(bootstrap_options = "striped")
```


<!-- ## seat share -->




<!-- ```{r} -->


<!-- fam <- readxl::read_xlsx("D:/cpr/misc/family_size.xlsx") -->


<!-- ``` -->


<!-- ```{r} -->

<!-- ggplot(fam, aes(n_adults,Percent, fill = factor(Location, levels = c("India","Delhi")), label = Frequency ))+ -->
<!--   geom_bar(stat= "identity", position="dodge")+ -->
<!--  colorspace::scale_fill_discrete_qualitative(palette= "Dark 2")+ -->
<!--   #geom_text(position = position_dodge (width =1), size =3.5, vjust = -.2)+ -->
<!--    labs(title = "Distribution of Family Size: India and Delhi", y = " % of families", x = "Number of adults", fill = "Election")+ -->
<!--   # ylim(0,60)+ -->
<!--   # scale_fill_manual(values = c("BJP" = "orange", -->
<!--   #                               "AITC" = "darkgreen"))+ -->
<!--   # scale_x_discrete(labels= areas)+ -->
<!--     theme_minimal()+ -->
<!--   theme(plot.margin = unit(c(.5,.5,.5,.5), "cm"), -->
<!--         legend.position = "bottom", -->
<!--         plot.background = element_blank(), -->
<!--         # plot.title = element_text( size = 18, family = "serif"), -->
<!--         # axis.text.x = element_text( size = 10), -->
<!--         legend.title = element_blank(), -->
<!--         #legend.text = element_text(size = 12), -->
<!--         axis.text = element_text(face = "italic"), -->
<!--         #axis.title = element_text(vjust = -1, size = 15),         -->
<!--         axis.ticks = element_blank(), -->
<!--         panel.grid.major = element_line(color = "gray50", size = .5), -->
<!--         panel.grid.minor = element_blank(), -->
<!--         panel.grid.major.x = element_blank(), -->
<!--         #  axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)), -->
<!--         # axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)), -->
<!--         axis.line.x = element_line(), -->

<!--   )  -->

<!--   #geom_histogram()+ -->
<!--   #facet_wrap(~Location) -->

<!-- ggsave("D:/cpr/misc/family.png", width = 6, height = 4) -->

<!-- ``` -->

##
 
 
## vote share historical


```{r}

vs <- read.csv("D:/cpr/elections/TN/vote.csv")

names(vs) <- c("party", "1967","1971","1980","1984","1989","1991","1996","2001","2006","2001","2016","2019")

vs %>% ungroup() %>% pivot_longer(-vs$party)

vs$
```










